%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.

%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}
	
	

\name{\cNobleTwo{}}

\bigquote{``Magic is not a practice. It is a living, breathing web of energy that, with our permission, can encase our every action.''}{-- DOROTHY MORRISON}

You hail from a long line of servants of the realm, giving talented rule and sound decisions for generations. A part of your family's ancestry also includes ties to a far reaching organization, one heard in fearful whispers, \bMagicMob{}. Have pride in your ancestors and in your self for you are one of the nobility, trained from birth to guide the path of your world's future. You hold the position of Junior Secretariat of Arcane Research, a fairly prestigious position, that you \emph{earned}, and were not simply given, though the earning included favors for \bMagicMob{} every so often. 

On the other hand, qualified may not be necessarily said of your ranking superior the Secretariat of Defensive Measures, \cNobleOne{\intro}. For gods sake, he does not even have the ability to do magic. You can't believe that his family's influence was so far reaching as to allow him to remain alive in spite of that, let alone to let him become a ruler. Really, a ruler of \bMagicWorld{} without magic? What nonsense! In all honesty you are much more qualified for the position, but the only way you can think of making this happen in your lifetime would be if a vote of no confidence could happen in an emergency situation. 

Oddly enough, an emergency situation has brewed all on its own. Your position has made you privy to a rather dark secret plaguing your world: the weave is becoming unstable, which will lead to the end of your world if it is not fixed. Fortunately, your mages have recently found a possible solution. Two of your top researchers have found signs of something in another universe that could be able to stabilize your world. They have been able to create small temporary portals to this other universe so you and your superior gave the go ahead to create a larger portal to send in a team to get the stabilizing artifacts. Maybe in light of all this, you can prove your own abilities. Or even indicate \cNobleOne{}'s lack of them. And then, sweet, sweet power...

Now, everyone has vices, and you are no exception. You are fond of the occasional, well, intoxicating experience. So you occasionally talk with members of the \bTechMob{}... And maybe one day, you let them in on these portals between universes. You know - it got you in their good graces. And so, in addition to the official stuff passing over the border, some other stuff has been going through. You were able to send a copy of the minor portal ritual to your criminal connections resulting in cross universe criminal connections being made somehow. And not only that, but you've learnt they have equivalent drugs over there. Maybe even better ones... You have been given the task of picking up a package of drugs from a member of \bTechMob{} and delivering a similar package to the other side's member. Better not get caught with that, might jeopardize your ability to gain \cNobleOne{}'s position.

Unfortunately, there are limitations to this connection to another world. Drugs aren't enough to solve every problem. Your magical spells apparently don't really work well there. You know, maybe \cNobleOne{} would fit right in over there... It would be great if you could make all your magic work when you visit them. No fun if you're stuck with the abilities of a fish if you were to go visit.There didn't seem to be any obvious reason why this would happen and so you asked the mages about this, but they kind of brushed you off in the excitement of their research. However, you're pretty sure you have some idea of how to do this by yourself. Maybe you can even finish and get it tested out today. 

And so, this morning you all got together to test the ultimate connection between the worlds. The connection that will finally bring in the last stuff needed to save the magical world. Would be such a pity if the world were to end. 

The ritual was initiated, with a flash of lemon, and a feel of sweetness several people appeared and the room has changed. The walls are a blend of the good ole stone and some sort of metal, and your mages' ritual areas now have a weird mirror image on the other side of the room. And there's a mess everywhere. This world-crossing isn't exactly as glamorous as you had imagined. 

You do hope that the mages actually know what they're doing. This does seem a bit more chaotic of a merging of worlds as you had expected. And they do seem to occasionally have inter-personal issues with each other. Better make sure that they actually agree with each other at least enough to finish the saving of the world. 


%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Keep your people in line
  \item make sure \cMageOne{\intro} and \cMageTwo{\intro} do their job
  \item Save \bMagicWorld{}, and ensure the world doesn't end. 
  \item Organize the speeches occurring at T+1:00 and T+3:00
  \item Usurp \cNobleOne{\intro}
  \item Investigate this Technological World and figure out how to make magic work there
  \item Make the drug exchange
\end{itemz}

\begin{itemz}[Notes]
	\item Your magical affinity is sound. You can hear very high pitched sound if you concentrate.
	\item You start the game with 50 gold. 
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cNobleOne{}} Your boss. Whether he's competent or not is another story
  \contact{\cMageOne{}} The head mage
  \contact{\cSciOne{}} A fellow mob member, but in the technical world
\end{contacts}


\end{document}
