%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}

\name{\cNobleOne{}}

%% This sort of use of \updatemacro is covered in
%% Extras/README-namemappings.
\updatemacro{\cNPC}{
  \unknownplayer %% doesn't know what he looks like
  }

%% quote examples
\bigquote{``Use this macro for large quotes of prose and such.  It
justifies everything like a paragraph, except with no
indentation.''}{-- The Author}

\cenquote{``This macro is good\\ For shorter quotes\\ Or things like
song lyrics:\\ It centers.''}{-- The Author}


%% \TODO outputs to the page and the terminal.  It is used for
%% reminders of future work, and a convenient way to build a short
%% outline for a sheet in-progress.
\TODO{This is a test character sheet.}

%% Using a Char macro with an empty argument, like \cTest{}, will
%% produce the \usual namemapping (see Extras/README-namemappings).
%% Introduce a character with \intro, e.g. \cTest{\intro}, to get a
%% more full name.  \intro can be used whenever it fits into the text
%% flow.
<<<<<<< HEAD
Your friend from out of town, \cSomeGuy{\intro}, called you up one
morning about a week ago.  \cSomeGuy{} told you to meet up with this
person named \cNPC{}, whom you've never met.  \cNPC{}, whose full name
is \cNPC{\intro}, is supposed to be really awesome and have a package
for you.

%% You can skip the advanced namemapping commands, and instead use
%% \full, \fullplain (full name without prefixes or suffixes),
%% \formal, and \informal.  You can also nest these inside identities,
%% such as \nick{} (see Extras/README-identity).
That bears repeating: \cNPC{\nick{\informal}}, whose full name is
\cNPC{\full}, is supposed to be really awesome and have a package for
you.

%% For pronouns and other gender-dependent words, you can use the
%% pronoun commands defined in Lists/char-LIST.tex to automatically
%% control them based on the character's gender.  For example,
%% \cTest{\They} will produce He, She, It, or He/She, based on
%% \cTest's \MYsex field.  You can define your own pronouns in
%% Lists/char-LIST.tex, as well.
\cSomeGuy{} is a pretty good friend.  \cSomeGuy{\They} used to be your
college roommate.  When \cSomeGuy{\they} called you up, you were
pleasantly surprised to hear from \cSomeGuy{\them}.

%% \me{} produces whatever the argument to \name{...} is.  If, like
%% usual, the argument was a char Macro, \me{} is an alias for that
%% macro.
Lots of people think your name, \me{\intro}, is funny.  You're not
sure why; you think it's a fine name.



=======



BEHIND ENEMY LINES: A SECRET EGALITARIAN MECHANIST AMONG HIARACHICAL MAGICIANS

Your parents tried their best to give you a normal childhood, but you were a sharp kid. You discovered magic the same year you found out that Santa wasn't real. But it was worse. Magic is real, and you are the only person who does not have it. In a world ruled by magic, having no magic is punishable by death at birth, even though many commoners' powers are as simple as liting a candle or summoning a breeze. You, however, are heir to a prominant and powerful family of archmages. Your family's name kept you alive, but you had to find your path on your own. In order to make up for your lack of magic, the link between mind and matter, you mastered mind and matter in their own right.

When it came the time to taking over your father's role in the ruling government, you did surprisingly well. The noble hierachy is formed based on magical power a long time ago, but over the years it has become much more. Personal prowness in court is a thing of the past. Today, money and influence rule. The nobles, while most revered for their might in magic, seldmly find use for their talents. On one hand, mind magic is strictly forbidden, and there are amulets to protect unsuspecting victims from such acts of malfeasance. On the other hand, using physical magic is as rude as throwing a punch, and no noble worth their feafdom would ever be caught doing so in court. The nobles fight with dueling canes. For magical matters, no demonstration is never necessary, and you have the best mages to council with. You could almost forget your own lack of magic, but for the constant reminder of your peers.

Your head advisor and family servant, SERVANT, looked after you your entire life and taught you by example important virtues such as temperance, diligence, and kindness. Ironically, he is secretly a hormonculous. You found out years ago when you noticed that he does not bleed red and has the genitals of a tennis ball. You really never cared after the initial shock, for he is still the same person, still as capable of reasoning and emotions, and full of love for his fellow humans.

Your lietunant, POLI2 is also capable but has no emphathy for those less gifted in magic; he is from a family with limited influence but has no limit to his ambition. He is nominally under your patronage, but he has no respect for "lesser" beings and has made it clear on many occassions. Sometimes you wonder if he is a socialpath. Perhaps it is only his obssession with decorum keeping him from stabbing you in the back and taking your worldly possessions. Unfortunately you needed someone for administrative magics and he came highly recommended by several sources. 

You manson has a backup heating and ventilation system designed by your grand father that runs on not magic but water steam. He was a very powerful mage but was also very interested in machinary, especially after his retirement. He spent a lot of that time teaching you action and reaction, leverage and torque. He believed that magic should be servant to humanity rather than his master.Your younger self studied machinary with ferver and found solace in it. You caused quite some commotion when you showed up at a in your steam powered mobile one day to show that you can manage without magic. It was a childish act looking back now, but sometimes you wonder if there is another world where everything is done with machinary rather than magic. Perhaps there people are judged by their virtues rather than their magic abilities.

It is natural that you've decided to fund the research in parallel worlds. You've taken it as a pet project, little did you know it will be crucial to saving your world one day. The thing that they call convergence now in the news has been known among the nobles for some time. It is mostly a localized loss of magic. The mages have found out that it is the effect of a universe similar to ours, but without magic, drifting too close, and affecting the deep magic that is weaved into our world. The only way it seems to prevent amegedon is to cause the two worlds to diverge by taking vital components out of that world and merge them with ours so that there is only one copy of them. You were already in charge of this particular research on parallel universe, and it needs only a small team anyway because the portal cannot let too many people through at a time, so you ended up in charge of the most important and desperate mission in human history. You have the most brilliant mages and a crack team of rogue operatives at your disposal. NOBLE 2 might be a problem, but you mustn't show fear or weakness because if that coyote can sense it he will tear you apart. They say nobles do whatever they want, but it's largely an illusion, and when it comes to other nobles you interact with, you are less free than the commoners.

On the other hand there is MAGE 2 who is one of the mages studying the parallel universe. Common people only use magic as tools to an end. THEY loves and understands magic the way you do machinery. You have a feeling that THEY does not care that you cannot cast magic, as long as you can understand and discuss it on an abstract level. However the chasm in your social status prehibit you from showing too much interest in THEM. Perhaps you would at least get to know the person better, because you might not get another chance after today.

The mages can only open the portal when the two worlds are extremely close, namely four hours before convergence. It is not much time for such a high stake operation. You want to have hourly all hands meetings, lead by you and NOBLE2, at least for the first two hours. The mages need to have a sound plan before the first meeting for you to approve of and brief everyone with. You have also invited PALADIN to perform hourly services to keep the moral up. You do not personally care for a religion that approves the killing of magicless infants and plan to get smoke breaks during the serivices.

description of the last 15 minutes 

Now that there is firm evidence that a world can exist without magic, perhaps now people will believe that it is not magic that makes one human, and that the infantcides can finally stop. You don't know PALADIN well, but he is the spiritual consilor of this unprecedented mission. Perhaps he will have an enlightened view, too. You would like to convince him to pardon the magicless in his scheduled sermons. You must also talk to the mages' counterparts and find out more about their machinaries. The ones you have seen can crudely imitate magical effects at best, but in the parallel universe they seem to be used for everything your people do with magic, including opening the portal. You believe everything that takes place here today will have lasting influence in your society at large, if the society continues to exist that is.

add rogue


>>>>>>> origin/master
%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Things to do
  \item Governments to topple
  \item Worlds to dominate
\end{itemz}

\begin{itemz}[Notes]
  \item You were born in London.
  \item You went to MIT, and never left.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cNPC{}} This person you've never met.
  \contact{\cSomeGuy{}} Your friend from out of town.
\end{contacts}

\end{document}
