\documentclass[char]{guildcamp3}
\begin{document}

\name{\cPaladin{}}

%% quote examples
\bigquote{``Use this macro for large quotes of prose and such.  It
justifies everything like a paragraph, except with no
indentation.''}{-- The Author}

\cenquote{``This macro is good\\ For shorter quotes\\ Or things like
song lyrics:\\ It centers.''}{-- The Author}

You were born the second son of a rich, upper class family. Though not of noble blood, your family name was still highly esteemed... at least before your mother ran off with one of the family's servants and never returned. You were only six years old at the time, so you remember very little of her. However, your stern father made sure to exclaim often about her sins and flaws of character while in your presence. She had no concept of duty or order or the sacred duty to one's class and bloodline. He would scream at the wall as he tore down her portraits and smashed her tea sets that she was at that very moment diluting our bloodline with the scum of the earth, debasing herself before the gods.

When you attended school, the other children whispered about you, saying your blood was tainted from being the son of a whore. Even as you grew older, colleagues would immediately look down on you, even those of lower class, as soon as they heard your family name. You had to be rid of it, that wretched brand upon your back.

Your father died when you were 22 years of age, while you were stagnating in your position in the financial department of your brother's manufacturing company. Your eldest brother inherited the family home, but you were left your father's collection of theological tomes. Your faith became an escape. You locked yourself up in the tower of your family home, whiling away the hours reading dusty scrolls of dogma and prophecy. It all started to make sense to you. Moral decay and failure to please the gods was the reason for your family's misfortune. It was time to break the generational curse, to make things right in the world.

On your 23rd birthday you dedicated yourself to the Church and entered the seminary, intensely studying the scriptures and the blade, the ancient art of the paladins, willing to defend the proper way of things with your body and your life. The gods gave you the gift of trancing, allowing you to commune with them more deeply, showing you that your actions and intentions have been proper. You took on a new name when you became a full-fledged Paladin, and the cleansing was complete.

Even after completing your official studies, you continued to immerse yourself in the ancient writings and epic poetry of seers and holy people, leading you towards the truth that only you seemed to see. It was right there in front of everyone's faces, but the people in their debasement preferred not to see it. All of the scriptures pointed towards the fact that everything was leading your world towards its end, when all would be judged before the gods. All of the signs were there. The high blooded were mixing with the low blooded, diluting the power of magical ability. The people, even those of high class, were brushing off their duties to the gods. Mere homunculi, created beings without souls, were being treated like men. There was even talk of atheism among the scholars! Society was coming to ruin!

Perhaps the most glaring example of the ruination of society was the fact that \cNobleOne{\intro}, a person with no magical ability, held the high position of Secretariat of Defense! He was of noble blood, but it was a slap in the face of the gods that such a being--who could really call him a man?--was exalted to this degree. His parents should have put him away as soon as they realized, but instead they educated him, pushing him towards one of the highest positions in the land with their influence. The mother had probably whored herself out to the lowest of the low to produce such a vile insult to her nobility.

When you found out you had been nominated as representative of the church to a special Convocation of Nobles in which \cNobleOne{\they} was at the head, you initially sneered. But you were no fool. You had heard the whisperings about disasters ands strange happenings across the globe, portents that the end was near. You narrowed your eyes, but agreed to go to their meetings. You found out that they intended to stop what was already in motion. Such blasphemy! They intended to exalt themselves, saying their will was above that of the gods, to extend their decaying, morally putrescent society.

It was up to you to make things right. You agreed to participate in their endeavor, with the intent to undermine them in their actions. It must be secret, though, for if they were to discover your true intentions they would send you away immediately. You have been living in their base for the past few weeks as they've been perfecting their portal device to make contact with the other world they discovered, hoping to use something they find there to stop the deterioration of your own universe. You must be subtle, appearing to do what they tell you to do, while secretly sowing discord and sabotaging their aims, while at the same time making attempts to convert unbelievers to the truth. Though you know judgment time is near, it is still your hope as a paladin to purify as many as you can before that time comes.

When the mages finally made contact with the other universe, just a few minutes ago, things did not go as planned. A strange feeling came over your entire body, feeling for a moment like you were in two places at once. All the hairs on your back stood up like you were in the presence of a spirit. Then there was chaos. The base was a mess, and the very walls seemed to be melded together with strange materials. And then there were the people. The doubles. Everyone at the base came face to face with someone identical to themselves, thrown together with them from the world parallel to your own. You know very little about them as of yet, but from what little information you have acquired, you are horrified. None of them have the aura of magical ability around them and they have no Church representative among them. What debased sort of world must they come from such that the gods are so disgusted with them that not even one has been gifted with magic? It must be a horrifyingly evil place. It is obvious to you that it is now its proper time for demise as well, so you want to ensure that neither side succeeds in saving their world.

But you must not dwell too much on their world. You have only hours remaining to ensure that the Convocation does not succeed in their task. It seems that people are gravitating towards their doubles, so you must try to sow discord between them, for their cooperation will lead to your failure.

In addition to this, you must enforce devotion to the gods and proper behavior for one's class and bloodline, while attempting to convert as many as possible, perhaps even those from the other universe, and bring those who have backslidden back into the embrace of the gods. You must also present a sermon after the first series of speeches given by the politicians and nobles of both worlds. Hopefully it will compel those listening to return to their prayers and seek you out for religious guidance. You should hold prayer and worship sessions, encouraging listeners to attend.

You may also at some point be compelled to perform wedding for those desirous of being bonded in the afterlife. It is your desire to only marry those who have the proper devotion to the gods, but you will have to perform the ceremony if requested to appear compliant.

In order to maintain your cover, you must recharge mana for Convocation members as they request by going into a trance and communing with the gods. Even if this were not the case, you would still want to commune with the gods at this time, as it is the rightful end of your world. And to those who refuse them... may the gods have mercy on their souls! 

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Ensure that the Convocation does not succeed in saving either universe by sowing discord between doubles and whatever else you can get away with without blowing your cover.
  \item Convert or return the backslidden to devotion.
  \item Preach to the masses after the politician's speeches.
  \item Enforce scripturally proper behavior for one's class among the Convocation members.
  \item Recharge the mana of those who request it to appear compliant if you can't get out of it.
  \item Regularly commune with the gods to aid you in your tasks. These trances will be more unpleasant for you the more you comply with recharging mana to aide Convocation members.
\end{itemz}

\begin{itemz}[Notes]
  \item If you know someone to be religious, you can compel them to confess the answer to a single yes/no question as a part of their devotion. This may be helpful in your tasks.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cNobleOne{}} Secretariat of Defense. He has no magical ability. In your opinion, he doesn't deserve the powerful role he has, despite his noble bloodline. However, you are subject to his orders and will do so grudgingly to maintain your cover.
  \contact{\cNobleTwo{}} The Undersecretariat of Arcane Scholarship. 
  \contact{\cSpecOpTwo{}} Your double from the other universe. A godless member of base security. You hope to convert \cSpecOpTwo{\them} to the faith.
  \contact{\cMageOne{}} A mage who helped to create the portal to the other universe.
  \contact{\cMageTwo{}} A mage who helped to create the portal to the other universe. 
  \contact{\cRogueOne{}} A member of base security.
  \contact{\cRogueTwo{}} A member of base security.
  \contact{\cServant{}} A \cServant{\human} who follows \cNobleOne{} around. Probably his servant, based on his clothing and manner.
\end{contacts}


\end{document}
