%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}

\name{\cPoliTwo{}}

%% This sort of use of \updatemacro is covered in
%% Extras/README-namemappings.
\updatemacro{\cNPC}{
  \unknownplayer %% doesn't know what he looks like
  }

%% quote examples
\bigquote{``Use this macro for large quotes of prose and such.  It
justifies everything like a paragraph, except with no
indentation.''}{-- The Author}

\cenquote{``This macro is good\\ For shorter quotes\\ Or things like
song lyrics:\\ It centers.''}{-- The Author}


%% \TODO outputs to the page and the terminal.  It is used for
%% reminders of future work, and a convenient way to build a short
%% outline for a sheet in-progress.
\TODO{This is a test character sheet.}

%% Using a Char macro with an empty argument, like \cTest{}, will
%% produce the \usual namemapping (see Extras/README-namemappings).
%% Introduce a character with \intro, e.g. \cTest{\intro}, to get a
%% more full name.  \intro can be used whenever it fits into the text
%% flow.
You cannot believe they put a pacifist in the position of secretary of defense. POLI1 did not even serve in the armed forces. Another sign that this great country is losing its edge. Everybody thinks that we have finally achieved the peace of our time. But you know it wouldn’t last, which is why as the undersecretary of defense you have pushed for and overseen the “Sky Net”, a network of defense satellites covering the near earth space against relativistic missile attacks. It is your life’s work, and you sleep well knowing that none can sneak up on your beloved homeland. Perhaps this is the peace of your time. 

You should have known better. Credible reports started coming in of paranormal incidents, and the scale has been increasing exponentially until just short of natural disasters. Possibilities of foreign sabotage was quickly ruled out because the incidents were affecting every major player. The scale has been increasing exponentially. It sickened you to see Sky Net turn into distant fireworks due to malfunctioning navigational systems. It is going to be near impossible to get funding for it again, especially with POLI1 against your idea of military spending. However if POLI1 were somehow out of the way though …  After all, it would do this country a great service to have a real general in charge of her defense.

While the world is falling apart around us, the Secretary-General formed a high priority task force to solve this issue.Scientists scrambled to find an explanation while spec-op’s procured info and equipment that is otherwise unavailable. A pair of researchers formerly working on parallel universe theory claim that our world is feeling the tidal effects of a parallel universe drifting too close to us. The eventual passing in the 5th dimension will tear us apart, unless we tunnel to them via a “portal” first and remove several key artifacts. You are giving them benefits of the doubt for now, because their demo of  a partial portal was very impressive. Besides, other worlds full of people and resources? It is just too much of an opportunity as well as security risk to overlook. 

Scientists estimate they can fully open the portal four hours before the eventual passing, and the fate of the world rests on the success of the spec-op team locating and retrieving all artifacts in time. It will supposedly make the two worlds diverge enough for both to survive. It is therefor imperative that you keep your people in line and on track. POLI1 might be a stickler for rules and meetings, but you agree they are necessary in this case, as it is too easy to lose track of time and squander the remaining hours. The scientists  are required to come up with a sound plan of action depending on the portal condition, to be signed by you and POLI1, within the hour of the portal opening. You will also lead all hands mission update with POLI1 each hour on the mark. 


When the portal opened though, something went awry. There was a flash, a sense of wrongness and a taste of red, and your surrounding was somewhat … transformed. Instead of clean and efficient design of a modern military base, it is in certain places decorated like a museum piece of a renaissance era living room. What’s more, random people appeared out of nowhere. But they are not entirely random. They look just like members on your team. You even spotted yourself in medieval clothing — and you cut quite a figure even in those antiquated uniforms. If you are not hallocinating, this must have something to do with the parallel universe. Perhaps they never had industrial revolution? You also see the weapon trafficker that you court-martialed, but he/she is not your problem, but your doppelganger’s. 

The worst thing is that most of the equipment are malfunctioning. You believe this is the effect of the parallel universe you are seeing. The scientists will be too busy with our primary objectives of saving the world, but you know a thing or two about science, and it won’t hurt to try getting some of the equipment working again. After all, you don’t want to be caught defenseless should these doppelgängers turn hostile.


With great perils come great opportunity. Perhaps it is your chance to make a move against POLI1 as well as saving the world. If you succeed, you will have all the influence you want to implement the mighty defense infrastructures you have thought up over the years.




mempack of rogue 1.
This is the weapon trafficker you caught during the war. ROGUE hoarded spare weapon parts and smuggled them back home to supply the mobsters. The mobster scene got so out of hand that the national guard had to be called. You only caught ROGUE towards the end of the war because supplies were running low and ROGUE’S unit kept running out of spare parts. You personally chaired ROGUE’s court martial, and watched his/her execution with great satisfaction.



%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Things to do
  \item Governments to topple
  \item Worlds to dominate
\end{itemz}

\begin{itemz}[Notes]
  \item You were born in London.
  \item You went to MIT, and never left.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cNPC{}} This person you've never met.
  \contact{\cSomeGuy{}} Your friend from out of town.
\end{contacts}

\end{document}
