\documentclass[char]{guildcamp3}
\begin{document}

\name{\cPoliOne{}}


%% quote examples
\bigquote{``Only the dead have seen the end of war.''}{-- Plato}



%% \TODO outputs to the page and the terminal.  It is used for
%% reminders of future work, and a convenient way to build a short
%% outline for a sheet in-progress.

%% Using a Char macro with an empty argument, like \cTest{}, will
%% produce the \usual namemapping (see Extras/README-namemappings).
%% Introduce a character with \intro, e.g. \cTest{\intro}, to get a
%% more full name.  \intro can be used whenever it fits into the text
%% flow.
Your made your career by managing crises and being on the winning side. Your proudest achievement was the peace signing between warring members of the "Cooperative" Plurality of Nations. But it wasn't all smooth sailing as the public was lead to perceive. You have witnessed humanitarian disasters, negotiated with war criminals, and everyone on your team has had to make great sacrifices, sometimes the ultimate kind, before there could be a happily ever after. At times you wonder if humans are only a step above animals. 

You've seen enough evil to last a lifetime, but, frankly, organized crime takes the cake. You've done some side work outside of your official career, privately investigating the mob's influence on Terra. The mob showcases the worst of humanity-- drugs, stealing, murder, more drugs . . . It's revolting how much of your world has been corrupted by crime. The mob has infiltrated even the scientific community to falsify a handful of research projects, turning the academic world's strict code of ethics into a joke. It was the mob's atrocities that propelled you to turn to religion and seek divine guidance. You want to know why humanity is tested mercilessly through one crisis after another. You keep your religious interest a secret, because it is uncommon for a public figure like yourself to openly subscribe to religion, in a science-focused society like yours. 

Over the last decade, you've been in the capital navigating the relatively benign waters of partisanal maneuvers. That's not to say the capital doesn't have its share of back stabbing, but your years on highly volatile diplomatic and intelligence operations have sharpened your survival skills and killer instincts. Many of your fellow politicians stick to ships that are clearly sinking, but never you. Your latest break was supporting the current Secretary-General of the Plurality during her election and your appointment as Secretary of Defense following her inauguration.

But it is never that easy. There is always another crisis. For a year now, you've been receiving credible reports of paranormal incidents. The scale has been increasing exponentially until just short of natural disasters. Possibilities of terrorism were quickly ruled out, because the incidents were just too bizarre. The Secretary-General formed a classified task force, while keeping the news from the public at your insistence. Scientists scrambled to find an explanation, while spec-ops procured info and equipment that is otherwise unavailable. A pair of researchers formerly working on multiverse theory claim that our world is feeling the tidal effects of a another universe drifting too close to us. The eventual passing in the 5th dimension will tear us apart, unless we tunnel to them via a \emph{portal} first and retrieve several key artifacts. That sounds like hogwash at first, but you were impressed with what the scientists achieved with a partial portal so far. Besides, it is the best lead by far, and in the nick of time. 

Now, scientists estimate they can fully open the portal four hours before the eventual passing, and the fate of the world rests on the success of your team locating and retrieving all artifacts in time. It is therefore imperative that you keep your people in line and on track. The world might be ending, but that doesn't mean everyone should forsake the sociopolitical machinery that works so well. You require the scientists to submit a sound plan of action based on the condition of the portal, to be signed by you within the hour after the portal opens. You will also lead all hands mission updates at each hour on the mark. And you'll have to keep your eyes open for any sign of illegal activity; government intelligence suggests that one or more members of your team are somehow connected to the mob. Whatever happens, you won't let organized crime jeopardize the fate of the world. If there's any wrongdoing, you'll stamp it out.

Just now, when the portal opened, something went awry. There was a flash, a sense of wrongness and a taste of red. Random people appeared out of nowhere. Except they are not entirely random. They look just like members on your team. Wait, there's yourself in medieval clothing. They look ridiculous. If you are not dreaming, then this must have something to do with the parallel universe. Perhaps they never had industrial revolution? And \cTech{} is in some sort of religious clothing. Is God common in the multiverse? Is it the same one true God? Perhaps you can find out under the guise of formal investigation. That would be quite a theological break through.

As you look around, your surroundings are also somewhat \ldots transformed. Instead of clean and efficient modern decor of a secret research facility, it is in certain places decorated like a museum piece of a renaissance era living room. In fact the decors appear quite ornate and authentic. You are tempted to collect some of the trinkets on display. For future research of course, though you are sure your brother, a big renaissance buff, would love to get his hands on some of these. After all, ownership becomes a little murky with these \emph{things} that have just appeared out of nowhere.

You also see some one who looks like the sibling of the weapon trafficker that you court-martialed, and oversaw the execution of, but \cRogueOne{\they} is not your problem, instead your doppelganger's. After all you doubt they are much different from the weapon trafficker you caught during the war.The sister of \cRogueOne{\intro} hoarded spare weapon parts and smuggled them back home to supply the mobsters. The mobster scene got so out of hand that the national guard had to be called. You only caught them towards the end of the war because supplies were running low and their unit kept running out of spare parts. You personally chaired the court martial, and watched her execution with great satisfaction.

The worst thing is that most of the equipment is malfunctioning. You believe this is the effect of the other universe you are seeing. The scientists will be too busy with our primary objectives of saving the world, but you know a thing or two about science, and it wouldn't hurt to try getting some of the equipment working again. After all, you don't want to be caught defenseless should these doppelgangers turn hostile.

Anyways you still have a world to save. The portal must have not opened properly. This is but another crisis in the bigger crisis that you have to manage. If you manage to survive this, perhaps you would run for the Secretary-General's office in next year's election.



%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Keep your people in line.
  \item Organize at least the first two progress reports.
  \item Discuss religion with \cPaladin{}.
  \item Prevent any and all illegal activity.
  \item Collect as many \emph{trinkets} from the other world as you can reasonably carry.
  \item Go investigate magic and see if technology can work in spite in of magic interference
\end{itemz}

\begin{itemz}[Notes]
	\item You start the game with 50 gold. 
	\end{itemz}
%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cPaladin{}} He looks like your technician, but is from the parallel universe and appears to be some sort of priest.
\end{contacts}

\end{document}
