\documentclass[char]{guildcamp3}
\begin{document}

\name{\cRogueTwo{}}

\bigquote{``A kleptomaniac is a person who helps himself because he can't help himself.''}{-- Henry Morgan}


\emph{Mission Statement:} 
As a result of a strange, supernatural phenomenon, the matter of our world is about to be ripped apart. Our mages have recently identified another universe that contains a stabilizer that can preserve us. Two mages, accompanied by you and several other figures, will enter this other universe through a portal to find the means of stabilization. Scout the other world, defend your team against any threats you encounter, and make sure the mages retrieve the stabilizer at all costs. You must return with the stabilizer within four hours in order to preserve our world.

\emph{Prior to entering the portal:}

"Rogue," they call you. That's what they call all of the members of your guild. Little do they know that the original meaning of "rogue"-- "scoundrel"-- fits you just as well. 

It's not that you're a bad person. But there's nothing more thrilling than gripping a bar of someone else's gold, than pocketing someone else's private letter. You steal from your friends, you steal from your enemies. You're not trying to hurt any particular person or accomplish any specific goal. It's not even about the money. It's the adrenaline. Sure, you've tried alcohol, drugs, all the usual vices, but even your high-stress job as a "Rogue"-- the job that's landed you in too many firefights to count-- can rarely match the rush of stealing. Fortunately, your professional work actually enables your obsession, from time to time. Your job, after all, frequently calls for you to scout important locations, to guard expensive treasures. So what if you pilfer a coin or a top-secret treaty? 

You keep random stuff you've stolen in your locker - who knows, maybe it's worth something on the black market? Maybe somebody even wants it right now.

Well, your capers are finally catching up to you. During one of your most recent assignments, you were charged with guarding the Countess of Tetra, who happens to own the renowned Ruby Diadem. You weren't greedy, of course; you wanted to extract just one ruby as a souvenir, but you got caught opening the Countess' vault. In the Countess' bedroom. You got caught by the Count.

Now, the Count and Countess are threatening to turn you in as soon as you return from this mission, unless you cough up enough money to placate them. You have some money saved up from previous heists, but you'd better scrounge up another 500 gold pieces right now, if you want to avoid life in prison. Thankfully, this could be a lucrative mission; you have to accompany some mages, nobles and paladins into a parallel universe, assist them while they're there, and get them safely out again. You don't get all the theory behind it, but you know one thing for sure-- you can dig up loot during this job. There's got to be exotic trinkets in the parallel world, and people from your own side will be bringing over plenty of gold. Hopefully, you can scrounge up enough actual cash-- merchandise won't do for the Count and Countess-- before this mission's over. You'll have to take risks, but a one-night stealing spree, a thieving tour de force, is the only way to save your skin.

Face it, you haven't been this excited in years.

You can already see a few obstacles in your way. \cNobleOne{}, the Secretariat of Defensive Measures, is coming along, and \cNobleOne{\they} might have a grudge against you.  \cNobleOne{\they}, after all, is one of those airheads with no magical ability, a fact that would have condemned him to death as a newborn if his last name was any less illustrious. Much of your family works at identifying magic-less infants and, well, eliminating them. Of course, you adore your relatives-- the parents who sacrificed to get you kids the best tutors, the sister who might become a famous mage someday-- and you're desperate to spare them all the shame of your kleptomania. On the other hand, you wouldn't be surprised if \cNobleOne{} is brusque with you, given what your relations do for a living. Try and keep the powerless twit happy, won't you? 

Family . . . Many years back, you made a mistake that you never told anyone about. You left the children, they're probably gone by now, and you haven't thought of those days often. But now, with all this talk of the end of the world, you can't help pondering what could have been . . .

\cRogueOne{}, the other Rogue assigned to this mission, also makes you nervous. \cRogueOne{\they}'s a tad sentimental for your tastes, and, more problematically, \cRogueOne{\they}'s been giving you weird looks for a while now. Did \cRogueOne{\they} see you stealing, somewhere along the way? Nah, \cRogueOne{\they} would have turned you in already, and-- the Diadem incident notwithstanding-- you're fantastic at covering your tracks. But you'd better be careful. If you do get caught today, make sure you have a good cover story.

Stealing isn't the same as it used to be ... It's better. And during some recent thefts, you've had weird moments of insight, perceptions about magic and reality that are normally way out of your pay grade.  Today, you have 4 hours to save yourself, doing what you do best. Go rogue.

\emph{After entering the portal:}
All right, something bad just happened. You were expecting to enter a new universe when you went through the portal, but you appear to have brought parts of your world's base with you. Worse, there's an alternate version of your team, right across the room. Same faces, but with completely different clothes. Everyone seems uniformly panicked.
You, however, haven't completely lost your cool. In the chaos that ensued right after entering the portal, you attempted to pickpocket the Undersecretariat of Arcane Knowledge. You couldn't quite pull it off though, and now the alternate version of yourself is giving you dirty looks. Time to start on those cover stories ...

\begin{itemz}[Goals]
  \item Keep the everyone, especially \cNobleOne{} and \cNobleTwo{} safe
  \item Figure out what on earth has happened to all your supplies with this change to the world
  \item Provide whatever help you can to the mages to get yourselves out of this mess. Maybe you can find some parts they need to build or operate the machine?
  \item Scout out the parallel world.
  \item Sell, barter and steal enough that you end the mission with 150 gold pieces. You will need to take these back to your family personally after the meeting. 
  \item Keep your kleptomania secret, especially from the nobles and the other rogue.  
\end{itemz}

\begin{itemz}[Notes]
	\item You are a kleptomaniac. This means that whenever you encounter a 0 or 1 hand bulky object which is sitting around without anyone paying attention to it, you feel a great need to pick it up and take it with you for a little while. If you don't get any such items every 15 minutes or so you become increasingly agitated. 
	\item Your magical affinity is light. You can make a surface reflective, or a shadow completely dark. It has proved useful for some of your missions.
	\item You start the game with 17 gold. 
	\item You can enter the Armory freely. It is well-stocked with useful items- one invisibilty cloak, one strength spell stone, one mind control device, and a knockout spell.

\end{itemz}



\begin{contacts}
	\contact{\cRogueOne{}} The other Rogue assigned to this mission. You are of equal level.
    \contact{\cMageTwo{}} A brilliant mage and your child, whom you haven't seen for ages.
\end{contacts}
\end{document}
