%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}

\name{\cRogueOne{}}

You were born into a lower middle class working family. Your parents loved you, but spent much of their time working to put food on the table. You were small for your age for much of your childhood, and were therefore the target of the crueler neighborhood children. You had few friends, and spent much of your time lonely. Your only solace was your close bond with your twin sister Sarah. She was kind and loyal and would bandage his wounds when he got into a fight. Though she was small and stringy, she had a loud and confident voice, and would sometimes manage to scare off bullies, embarrassed to be shouted at by a girl using such crude language. You would sometimes go out on adventures together, charming the birds and squirrels to do tricks and finding fun places to play. But then one day when you were both ten years old, Sarah went out to play and never came back. She had invited you, but you had a headache from a punch the previous day, and decided to stay home. You never truly forgave yourself for not being there for her like she was there for you. They found her body floating in the river three days later, her long golden hair shorn from her head. Law enforcement never managed to find the killer.

You became angry after that, enough so that even the boys who used to bully you were scared of the dark look in your eyes. You wanted revenge. You wanted to find the man who killed your sister and make him bleed and scream. You found some measure of solace practicing your fighting skills in back alley tournaments and even convinced some older boys to teach you how to hurt people properly. You spent most of your days skulking around the city, leaping across roofs and magicking yourself to fade into the shadows. You began to feel more in control, more powerful. One day you'd find your sister's killer. And you would be ready. But years passed, and you were nowhere closer to finding him. Eventually you were just going about your routine mechanically, conflicted, looking for some real meaning in your life. You even sometimes found yourself angry at your sister for leaving you. Everyone you ever trusted to help you left in some way. Your parents had to work, leaving you to mostly raise yourself. The schoolteachers left him to be beat up by larger children. And his sister left him when she was murdered. By the time you were in your late teens, you had decided that from now on, you were going to do everything for yourself, figure things out on your own. And you took pride in that. You could teach yourself just about anything, and through hard work and practice master it. You could support yourself and find a better way of living, all through your own efforts.

Eventually, you were observed in your wandering by members of the local Rogue's Guild, who thought you had some talent. They recruited you and took you in as an apprentice. You took great pride in your success rate in the jobs you took on from your clients, and your standard of living began to improve. You even managed to buy your own house, whereas your parents had to rent your childhood home. Higher and higher government agencies began to request your services. They saw you had talent. And finally, one day, the representative of the Convocation of Nobles showed up at your door. They had a very special job for you. You had to sign several documents and agree to a binding of loyalty before they would even give you the details.

You were shocked by what the representative told you. Just when your life had gotten better to some degree, though you were still somewhat lonely, here's the end of the world to bring things down. The Convocation had been called together to investigate the strange occurrences you'd been hearing rumors about, only to discover that the deep magic that sustains your world is unraveling, and it's only a matter of time before it falls apart altogether. You simply can't accept that this is the end for you. Like hell is this going to stop you, just when better things are within reach. 

You were tasked with protecting those who are attempting to stop the apocalypse by opening a portal to a parallel universe. You knew they were looking for something there that could save your world, though you didn't have a whole lot of details, just that you were to do everything you could to keep them safe, allow them to do their work, and acquire necessary items for their procedures in the manner of a rogue. And so you have been. You have been doing everything you can to make sure that everything goes smoothly in the secret base you've all been living and working in for the past few weeks.

However, you are a practical person. You know from experience that things don't always go your way, no matter how much you care about them, how much effort you put into them. For that reason, you've spent a lot of sleepless nights studying the magical texts and components around the base in the hope that you could create a one-way escape vehicle to another universe using a method similar to that the mages are using to make contact with the other world. You've always been a quick study, but you only know enough to make a one-way ticket to somewhere random. You want to build the device, just in case, but you will only use it as a last resort. You know you can handle burning bridges, but you're not reckless, Your highest priority is still saving your world, where you might someday find someone to love and spend your life with.

You knew what you were getting yourself into here, but you weren't expecting what happened when the mages opened the final portal. When they incanted the final words you saw a flash of darkness that seemed to burn itself into the back of your eyes and felt a rippling wave of energy pass through your body. Then everything was jumbled. The walls and the doors looked different. And items were strewn everywhere, mixed in with unfamiliar machinery. And then... you saw \emph{them}. Somehow you'd been dumped in this mixed-up place together with people from the universe you'd been trying to contact. And their faces were the faces of the Convocation members of your world. They \emph{were} them, but at the same time... not. The world they came from is alien to you, and now you have to work together with them if there is to be any hope of saving your world. And worse... it appears that your doubles are in a similar predicament regarding their world. You think back to your escape pod plans, which are ready to be put to use.

But you quickly return to your first priority. You will have to work with these strange people and their devices, but your loyalty is to your world. In these last remaining hours before what could be the end, you will follow the orders of your nobles and procure everything the mages need. But first you will need to perform some reconnaissance to determine the new state of things at the base. What items are still available and what new things have arrived from the other world. This is information your nobles need to know.

And now you're sure of it. You must find time to make the escape vehicle in between doing your other duties. With these new developments, anything could go wrong.

Despite how you've always presented yourself as confident and capable, under the surface you are starting to feel some doubts. Now that there is very little time remaining, you are starting to wonder whether it will really be possible for things to turn out okay. You have little experience with happy endings. You've never been very religious, but you are beginning to wonder whether you might receive some support from the gods. For this reason, you want to take some time in these final hours to speak with \cPaladin{} for spiritual guidance.

On top of that, you're feeling like you should get a few things done that you would hate yourself if you were to die without having experienced. Requited love, for one. In the short time since your worlds have combined, one of the people from the other world has caught your eye. Their name is \cPoliOne{}, and they hold a role similar to \cNobleOne{}, who is in fact \cPoliOne{\their} double. Though you have never felt a thing for \cNobleOne{}, who frankly makes you feel uncomfortable due to his lack of magical ability, something about \cPoliOne{} intrigues you. What the hell? It's the end of the world, isn't it? Find some free time to romance \cPoliOne{\them}. Hell, write \cPoliOne{\them} a love poem, present it to \cPoliOne{\them}, and convince them to go on a date with you if you both get out of this alive. 

And lastly, there is something that worries you. Every other person working with the Convocation appears to have a double among the people from the other universe. Everyone except you. Could this mean that you are in more danger than you already thought? If you have a double, what could have happened to them? Do you simply not have one? You feel like this is important information and are determined to find out the answer. Things are looking sort of grim. Maybe it's time for a drink.

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Work towards saving your world, though if the efforts appear to be failing, you may abandon this goal when the end is near.
  \item Protect the nobles from attacks.
  \item Do area reconnaissance for your nobles to determine how the base has been changed and the state of important/useful objects.
  \item As requested by nobles and mages, acquire items they need in the manner of a rogue.
  \item Figure out why you don't have a double.
  \item Create your escape pod, and use it if things go bad. But only use it as a last resort.
  \item Romance \cMage, write and present \cMage{\them} with a love poem, and get \cMage{\them} to agree to go on a date.
  \item Get spiritual guidance from /cPaladin{}.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cNobleOne{}} Secretariat of Defense. He has no magical ability. There was a lot of scandal over his appointment to this role. You don't understand how someone like him could do his job properly without magic, but will follow his commands, since you both have a common goal.
  \contact{\cPoliOne{}} The Secretary of Defense from the other universe, \cNobleOne{}'s double. You feel strongly attracted to \cPoliOne{\them|.
  \contact{\cNobleTwo{}} The Undersecretariat of Arcane Scholarship. 
  \contact{\cMageOne{}} A mage who helped to create the portal to the other universe.
  \contact{\cMageTwo{}} A mage who helped to create the portal to the other universe. 
  \contact{\cRogueTwo{}} A member of base security. He is a fellow member of the Rogue's Guild. Shifty fellow.
  \contact{\cPaladin} Representative of the Church who recently arrived. You want to talk to him for spiritual guidance.
  \contact{\cServant{}} \cNobleOne{}'s servant. 
\end{contacts}


\end{document}
