%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}

\name{\cSciOne{}}


\updatemacro{\cNPC}{
  \unknownplayer %% doesn't know what he looks like
  }

How did it get so far?

You were approached thirteen years ago, when you were still in university, by a politician who obtained a grant for you by pushing strongly. Too strongly. You were planning to explore commercial uses for Compound 9, which showed promise as a lightweight alternative to cement. Little did you know that Compound 9 was already making the rounds in the shadowy underworld. Dealers were touting it as a potent hallucinogen, while mob bosses wanted the government to sanction its creation for legal purposes, in order to secure a steady supply. They wanted your research to legitimize Compound 9, and they'd provide you funding and connections in return. You were fine with receiving help from the mob-connected politician-- after all, the scientific world is highly competitive, and, as a novice researcher, you were grateful for the leg-up. Unfortunately, your research showed that Compound 9 couldn't actually function as a building material. The mob forced you to fudge your results, and that's where the troubles started.

By now, the mob has too much dirt on you. They will cut you loose and expose without much risk to themselves, unless you do exactly as they direct. You research what they tell you to research, you report the results that they want. You fundamentally understand science, though, and you've veiled your projects with enough hedging and "confounding factors" that other academics haven't caught on. In the last few years, your position has gotten riskier than ever. Somehow, one of your mob connections passed you preliminary notes from another scientist, \cSciTwo{}, about a theory about parallel worlds. You cleaned up the notes and developed the ideas with your own perspective, and, at a biophysics conference at the capital city, you gave a presentation about a possible convergence between your universe and another. You got great feedback, and politicians offered you two times as much funding for further research as you had asked for. Meanwhile, \cSciTwo{} received no interest at all, when \cSciTwo{\they} presented \cSciTwo{\their} original ideas a few days later at a conference in Tetra.

Now, you're in charge of all the scientific research on the collision of the two worlds. The initial work was exciting-- cutting-edge equipment, handsome speaking fees, jet-setting off to conferences and top-secret meetings. But the tension's been building since you realized that \cSciTwo{} was right-- that there was really going to be a collision, and that you had set yourself up as the clearest candidate for field research. You have to enter the convergence, and you're scared to find what's on the other side.

But you can't even wallow in plain existential despair! Somehow, \cSciTwo{} got assigned as the other scientist on the field research team, and, though \cSciTwo{\they} is supposed to be smart, you really don't like \cSciTwo{\them}. \cSciTwo{\they}'s downright terrible to have in the lab-- awkward, unhelpful, and self-absorbed. For years you've heard the whispers that \cSciTwo{\they}'s hard to work with; if \cSciTwo{\they} treated the audience at the Tetra Annual Cosmology Conference the way \cSciTwo{\they} treats you, you're not surprised that nobody listened to \cSciTwo{\their} convergence theory. \cSciTwo{\Their} presence distracts you constantly.

Another doubt's been gnawing at you, too. What if \cSciTwo{\they} suspects you of stealing \cSciTwo{\their} work? You'd better really impress \cSciTwo{\them} today, prove your worth as a scientist, and make \cSciTwo{\them} believe that you could have come up with the convergence theory on your own.


To make things more complicated, \cSpecOpOne{\intro}-- your parent-- is assigned to this job for security purposes. The two of you haven't been talking recently. About a year ago, \cSpecOpOne{\they accused you of shutting \cSpecOpOne{\them out of your life, and \cSpecOpOne{\they} was right; you've been way too tense and secretive as pressure from this project ramped up. At the end of the day, though, you need to restore your relationship. Just hearing that \cSpecOpOne{\they} still loves you would make all your stress-- or at least some of it-- melt away. Unfortunately, your criminal activities complicate the situation. \cSpecOpOne{} is an ex-con with a history of human experimentation, the thought of which just makes you sick. But\cSpecOpOne{\they} got clean, and now nothing would hurt \cSpecOpOne{\them} more than realizing that you've fallen into an even shadier lifestyle. Whatever you do, you can't let \cSpecOpOne{\them} find out about your crimes.

As if this wasn't all complex enough, the mob has another demand for you. According to whatever limited communication the politicians have had with the parallel world, this other universe contains some substance similar to Compound 9-- also a hallucinogen, but more likely to have legitimate uses. The mob wants you to find and retrieve a large sample. Luckily, there's at least one other member of the mob on your team-- \cSpecOpTwo{\intro}-- and \cSpecOpTwo{\they}'s likely to help you. There also seems to be a parallel mob in the alternate world . . . Some things never change. If you're lucky, you can meet with some of the parallel mob's members and arrange a deal for the drugs, or you can finagle some other way to get the stuff. If you're unlucky, your mob might cut you loose tomorrow morning.

So you've got to research the convergence, get a drug sample, fix your family, and keep your dubious past under wraps. Anything else? Oh, right. Make it out alive.

\begin{itemz}[Goals]
  \item Get alternate version of Compound 9
  \item Convince \cSciOne{} of your ability and innocence
  \item Research the convergence
  \item Craft new technology as needed within the convergence
  \item Get verbal confirmation from \cSpecOpOne{} that \cSpecOpOne{\they} still loves you.
\end{itemz}

\begin{itemz}[Notes]
  \item You were born in London.
  \item You went to MIT, and never left.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cSciTwo{}} The annoying junior scientist on this mission.
  \contact{\cPoliOne{}} The Secretary of Defense.
  \contact{\cPoliTwo{}} The Undersecretary of Technology.
  \contact{\cSpecOpOne{}} Involved with security. Also happens to be your parent.
  \contact{\cSpecOpTwo{}} Involved with security. The only mob member on your team, as far as you know.
  \contact{\cTech{}} The technician who recharges your batteries. Might help you impress \cSciTwo{}.
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}

  \mTest{}

  \memfold{``Rosebud''}{Rosebud!  That was the name of\ldots the name
  of\ldots darn, you forget.}

  \startmembook{Book of Mempackets}

    \mempage{if you see something blue}{Hey, that's blue!  Oh, you
    remember, blue is your favorite color.  You really like blue
    things, especially blue tentacles.  You wonder why\ldots}

    \mempage{``Octy''}{Octy!  You remember Octy now!  She was your pet
    blue octopus when you were a young child living offshore.  Oh, the
    fun times you had!

    You used to go swimming and diving with Octy all the time.  This
    was years ago.  What happened?  You still can't remember\ldots but
    you know you haven't even thought of her since you were small.}

  \endmembook

\endtag

\starttag{abils}
  \ability{Amazing Powers}{You can do strange and amazing things.}{I
  do something strange and amazing.}
\endtag


\end{document}
