%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}
	
	\name{\cServant{}}
	
	%% quote examples
	\bigquote{``Use this macro for large quotes of prose and such.  It
		justifies everything like a paragraph, except with no
		indentation.''}{-- The Author}
	
	Your first memory is of the flame of mana rushing through you as the animation ritual was performed over your constructed body. Opening your eyes for the first time, you saw your first master, a high-ranking member of \bMagicMob{}. From the very beginning \bMagicMob{} made it clear that they \emph{owned} you and you could feel the force of the bindings they cast on you to compel you to do their bidding. Over time you came to know the reason for your existence. \bMagicMob{} needed someone to do their dirty work with no risk to themselves, with the added plus of being able to sculpt you for strength, so they were quite willing to finance the creation of a homunculus. Of you. You are tall and lined with muscle, with large hands fit for crushing, but with enough delicacy for more precise actions. Looking at yourself in mirrors, it appears that you have a very average looking face. Calculatedly average, so you will attract as little attention as possible given your large frame. You have a dull look to you, so people will not guess that you are up to something. In truth, you are quite clever beneath the surface. And though \cMagicMob{} do not treat you like it, you can use your mind to \emph{feel} wonder and sadness and love.
	
	But over time you learned to bury the emotions. Otherwise it would be too painful to do the things \bMagicMob{} makes you do, and to endure how they treat you. You are strangled with the bindings on top of bindings they work on you to make you obedient and complacent. At least on the outside. On the inside you still have a mind of your own, but you feel strangled by the hold of their cruel magic. When you are not out on a "job," they lock you in a cage in the basement of an old building on the edge of the city, and beat you when you are not successful, or if you take too long to get something done.
	
	For years, \bMagicMob{} has sent you out on a variety of different sorts of "jobs." Sometimes they just want a brute to send someone to the bottom of the river, or to convince someone to pay their debt and break some fingers. Other times they send you undercover in the role of a servant or laborer or cook, to get close enough to subtly assassinate a more dangerous enemy or collect information from powerful individuals, as well do errands such as move drugs and deliver secret documents. They even trained you in the art of potion making to be able to manipulate and kill their targets without being overly obvious.
	
	A few years ago, they sent you out on your first long-term mission. They pulled some strings to get you a position as the personal servant to \cNobleOne{}, Secretariat of Defense. There is a lot of scandal surrounding him and his position, given that he was born with no magical ability, when the noble lines are supposed to have the strongest connection to the deep magic. You've gathered over time that most such children are killed shortly after their birth, and that the sole reason \cNobleOne{} was allowed to live was because of his powerful parents. Somehow he managed to work his way up to the prominent position he holds today. Someone was probably pulling strings for him as well. Your "job" with \cNobleOne{\them} is to collect information on \cNobleOne{\them} and his actions as Secretariat and relay them back to \bMagicMob{}. Ultimately, you are bound to kill \cNobleOne{}, and you fear that you cannot hold it off much longer.
	
	As time has gone by, you have become increasingly guilty at having to convey \cNobleOne{}'s secrets to \bMagicMob{}. You have tried to resist the bindings, but eventually they painfully force you to do as you have been bidden. In fact, you have come to feel a strong sense of loyalty to \cNobleOne{}, to the point where you consider him your only real master. \cNobleOne{\they} is the only person who has ever treated you with kindness, almost on the level of an equal, though \cNobleOne{\they} is born of noble blood and you are \cNobleOne{\their} servant. Perhaps this is because grew up knowing what it was like to be despised and considered less than human for reasons entirely out of his control, just like you. Likewise, you both have a distaste for the Church, which teaches that those born without magical ability have no place in society and are less than human, as well as that homunculi are less than men and have no soul. You feel a sense of kinship with \cNobleOne{} over your shared history of mistreatment.
	
	There is truly something special about \cNobleOne{}, leading you to believe that he deserves his Secretariat position, that he is that rare person who genuinely cares about the underdogs and has the power to help them. Most people who had grown up in his position would have come out withered and cruel, but instead \cNobleOne{} became compassionate. You became determined to ensure that \cNobleOne{\they} is successful in his endeavors and find health and happiness. But at the same time you were overwhelmed by guilt for being forced to steal his secrets, secrets that could ruin him, and give them to \bMagicMob{}. And there was that last binding... you are horrified at the thought that your body will one day betray your morals turn on your master. And time is running out, since \bMagicMob{} seems nearly satisfied with what they have learned. There has to be some way to prevent it! 
	
	By the time your master answered an insistent knock in the night, it already took most of your willpower to hold back the binding. The messenger told \cNobleOne{} of an urgent formation of the Convocation of Nobles, regarding the recent rumors of disasters and strange portents in the sky. So your master packed \cNobleOne{\their} bags and left to meet with the Convocation, taking you along with \cNobleOne{\them}. They said it was the end of the world, that they are making their last efforts to save it, by entering another and bringing something back. You left from the Convocation halls to a secret base deep in the wild. It was here that humanity would make its last stand against the void, under your master's guidance. 
	
	Realizing the graivity of these circumstances, you are even more determined to ensure that your master succeeds in \cNobleOne{\their} endeavors, and you would give your own life to ensure that \cNobleOne{\they} come out of this alive and happy. You have decided it. Your first loyalty is to \cNobleOne{}, not \bMagicMob{}. Screw the bindings! 
	
	And then, as the mages made their final ritual to open the portal to the other world, an answer dropped right within your reach. When the portal opened, things didn't go as planned. Rather than opening a doorway, the portal expanded in an unstable way, causing the base location in each world to merge together in a haphazard way. There was a chill like a knife in your chest and a sound like a scream, and then everything was amiss. The building looked different, yet strangely the same. In places the wall seemed to swirl and melt together, and strange things were strewn about the floors. And then, there were the others, people who came from the other universe, pulled into this mess with the Convocation members. Oddest of all, and most promising, was that they appeared to be near doubles of your master's colleagues. There was even someone who looked just like you, bu the name of \cTech{}. Was \cTech{} a homunculus as well? You came to realize that this was highly unlikely, as you could feel no magic in any of them. But even your own double could not draw your attention away from \cPoliOne{}, your master's perfect match.
	
	You are now convinced that if you kill \cPoliOne{}, your bindng to kill your master will be broken, and you will be free to follow your own conscience. Though you can see in \cNobleOne{}'s eyes a longing for life in a world like the other, where those like him are accepted as equals, you will continue to support \cNobleOne{\them} in \cNobleOne{\their} endeavors, even if it leads to your separation. For you cannot follow \cNobleOne{\them} to that alien place. Homunculi run on magic, and if there is no magic there, you will die as soon as your mana runs out. 
	
	In fact, this may prove to be an issue even before \cNobleOne{} has to make \cNobleOne{\their} decision. No matter where you are, if you run out of mana, you will die. In order to help \cNobleOne{}, you must keep your mana levels up. You are capable of draining mana from people with magical ability, but you will probably only do this as a last resort, as it would reveal you to the others as a homunculus. Though \cNobleOne{} accepts you as you are, it is unlikely that the others would trust you if they knew your true nature, and cooperation is necessary to save the world from the mess it's in.
	
	Your other option to maintain your mana is to go to \cPaladin{}, who should give you mana as long as \cPaladin{\they} doesn't find out what you are, as that is a part of \cPaladin{\their} role as representative of the Church to the Convocation. You are not technically a member of the Convocation, but as \cNobleOne{}'s servant, you can say that it is necessary for you to have mana to serve your master.
	
	Unfortunately, the mob has been made aware of your current situation, and has given you additional tasks to complete. There are mere hours left to save the world and your master, yet you are also bound to facilitate the exchange of boxes of drugs between \bMagicMob{} and its equivalent in the other world. You must also deliver a secret file to \cSpecOpTwo{}, a member of base security and secret member of that other organization. You consider these tasks to be of lower priority, but even now you can feel the bindings pulling at you, burning you from the inside out.

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
	\item Do everything \cNobleOne{} tells you to do.
	\item Make sure \cNobleOne{} is successful in \cNobleOne{\their} endeavors.
	\item Work towards the common goal of saving your home universe.
	\item Kill \cPoliOne{}, your master's double from the other universe, in hopes that it will satisfy your binding to kill your master. Don't let anyone catch you.
	\item Deliver the secret documents the Mob has given you to \cSpecOpTwo{}.
	\item Facilitate the exchange of drugs between the Magic Mob and Tech Mob. Don't let anyone not in on the deal get a hold of them.
\end{itemz}

\begin{itemz}[Notes]
	\item If your mana level ever reaches 0, you will die.
	\item Your potions training may be very useful in attaining your goals.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
	\contact{\cNobleOne{}} Your master, the Secretariat of Defense, to whom you are intensely loyal. He has no magical ability.
	\contact{\cPoliOne{}} Your master's double from the other universe, who you must kill to satisfy the Mob.
	\contact{\cSpecOpTwo{}} A member of base security from the other universe. The mob has ordered you to deliver a secret file to \cSpecOpTwo{\them}. 
	\contact{\cNobleTwo{}} The Undersecretariat of Arcane Scholarship. He has an intense hatred for your master.
	\contact{\cMageOne{}} A mage who helped to create the portal to the other universe. You don't know \cMageOne{\them}.
	\contact{\cMageTwo{}} A mage who helped to create the portal to the other universe. You don't know \cMageTwo{\them}.
	\contact{\cRogueOne{}} A member of base security. You don't know \cRogueOne{\them}.
	\contact{\cRogueTwo{}} His official role is base security, but you know he's a member of the Rogue's Guild and a fence for \bMagicMob{}. He runs the black market. Shifty fellow.
	\contact{\cPaladin} Representative of the Church. You don't like him because he preaches that homunculi have no souls and are less than humans, but will need to go to him to replenish mana.
\end{contacts}


\end{document}
