%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}

\name{\cSpecOpTwo{}}


%% quote examples
\bigquote{``There are moments in life when it is all turned inside out--what is real becomes unreal, what is unreal becomes tangible, and all your levelheaded efforts to keep a tight ontological control are rendered silly and indulgent.''}{-- Aleksandar Hemon}

You couldn't be more honored to have been selected to be on the defense team for this expedition to save the world. Coming from a poor family, you'd never dreamed of such an honor. So when the secretary of defense himself, \cPoliOne{\intro}, asked if you'd come along as security of course you agreed. Of course, you didn't exactly expect it to work out this way, with discovering an entire parallel universe in which there apparently exist doubles of everyone. Upon this portal opening, you just saw a bunch of people - who all seemed to be somehow similar to those you brought. Strangely enough, you seem to be the double of the other world's religious leader, \cPaladin{\intro}. You were never a religious \cSpecOpTwo{\human}, never even went to church as a child. So who really knows what's up with that.

Now that this portal has opened, your security job becomes more important than ever for two reasons. First, well, there's a lot of new people and you need to make sure none of them harm your political figure, \cPoliOne{} Keeping them safe is your primary job after all. And second of all, this crazy portal seems to have thrown everything around. Who knows where all the parts you had so carefully stockpiled to ensure the scientists could finish on time are. At least you're pretty sure the three artifacts are still here. Regardless, this is going to be a cataloging nightmare. And then making sure no one steals the critical parts ought to be annoying. Or at least your boss, \cSpecOpOne{\intro} seems to think so. He's looking rather agitated now. 

But no one, not \cPoliOne{} or anyone else, knows your deepest secret. A secret that if they learned, they would shun you immediately for. Since you were a small child, you've had these 'spells' where you'll just kind of become unaware for a while. Officially, your parents called them trances and you had a severe case. Being poor helped you out here - no one expected the poor kid to do great in school or anything. And your parents always made sure to budget enough money to medicate you so you wouldn't have spells \emph{too} often during the day. Unfortunately, the medication only lasts for around 30 minutes, so you were always looking for a secret place to take your pills at school. And later at work. Occasionally someone would catch you and you'd be able to brush it off as headache medication or something, but your worst fear was always someone discovering the truth. Because if the officials knew about your state, you shudder to learn what would happen to you. Let's just say it certainly wouldn't be pretty and you probably wouldn't have a job anymore.

Getting back to the present, your job does provide enough money that you can take sufficient medication every day. Sometimes its a pain to do so in private, but being a secret agent, private is your specialty. All those years of hiding pill taking from your teachers finally paid off for this job. Unfortunately, you're running out of the pills today. You were planning to stop by the pharmacy this morning, but had no time to do so - now you've only got three pills to last you for the rest of the day - you'll have to find some way to get more. In the meantime, you'll need to make sure you don't accidentally give yourself away to your new boss, \cSpecOpOne{}. You're pretty sure he doesn't suspect anything yet, but you're just one spell away from outing yourself. 

Of course, the ultimate solution would be to actually find a \emph{cure} for the trances. A cure - a real one that would make it so you never had to take a pill again and never had another spell. You know some people have been working on it, and with the discovery of this new world perhaps someone there has had more luck. You'd do almost anything for such a cure. Hopefully someone here has one.  

The other thing you care deeply about is your family. They were never rich and while you get paid a decent chunk of money now, it's not enough to support everyone. So you occasionally do side jobs and the like to get a bit more. Selling official secrets seems to be a popular one - who knew people would pay so much for verification of some silly thing, like "\cPoliOne{} is a member of his local quilting group."? Whatever, as long as it pays the bills. 

In addition to your official duties as a security agent, you have some undercover business here today. If you're going to spend your whole life hiding, why not go full out? And so a while back you got involved with \bTechMob{}. There's some drugs here that you've got. Or at least had before the portal threw them into who-knows-where. And according to the mob bosses, they've got some even better drugs in the \bMagicWorld{}, the other world. And you're supposed to get together with to exchange those with the others. 

But your years of hiding paid off, and the mob-boss has given you a second package. You don't know what it is, just that it is \emph{very important} and that you are supposed to exchange it for another package with one of the Magic people - \cServant{\intro}. Come to think of it, how did that mob-boss know you were going to come across Magic people? Oh well, as long as you get paid. The boss conveyed that this was of utmost importance - exchange the package with \cServant{} or he'd have your head. But as long as you do exchange it, "Don't worry, I've got you \cSpecOpTwo{\informal}." 

%% Using a Char macro with an empty argument, like \cTest{}, will
%% produce the \usual namemapping (see Extras/README-namemappings).
%% Introduce a character with \intro, e.g. \cTest{\intro}, to get a
%% more full name.  \intro can be used whenever it fits into the text
%% flow.

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Ensure the safety of the politicians, and the technical world in general.
  \item Inventory the remaining supplies and ensure the resources needed to save the world are present.
  \item Find a cure for your trances.
  \item Ensure no one finds out about your trances.
  \item Make the mob exchange with \cServant{\informal}.
  \item Make the mob drug exchange with the whole group.
  \item Get 100 gold to send back to your family at home. Probably by selling secrets. You will need to personally bring this back to your family at home. They wouldn't trust anyone else with it and you don't trust the postal service (or any other people) to take care of them for you. 
\end{itemz}

\begin{itemz}[Notes]
  \item Assume you took a pill to prevent trances immediately prior to game start. In the chaos of the portal opening, no one noticed you. 
  \item You start the game with 12 gold. 
  \item You can enter the Armory freely. It is well-stocked with useful items- one cloaking device, one dose of steroids, one mind control device, and a sonic knockout device.

\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cSpecOpOne{}} Your boss.
  \contact{\cPoliOne{}} The Secretary of Defense. \cPoliOne{they}'s in charge today and you should protect him.
  \contact{\cServant{}} The corresponding mobster you must exchange things with for the special mission. Be sure you do this or the mob will have your head.
  \contact{\cPaladin{}} The religious leader of the Magical World. For some reason you're \cPaladin{}'s double. 
\end{contacts}


\end{document}
