%%%%%
%%
%% Character sheets live in this directory.  This file doubles as a
%% latex'able example charsheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Character macros (in ../Lists/char-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given character, which will generate
%% the charsheet's name (and print out lists of the characters stuff
%% at the end) as specified in char-LIST.tex.  However, you can also
%% just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[char]{guildcamp3}
\begin{document}

\name{\cTech{}}

%% This sort of use of \updatemacro is covered in
%% Extras/README-namemappings.
\updatemacro{\cNPC}{
  \unknownplayer %% doesn't know what he looks like
  }

%% quote examples
\bigquote{``Twenty years from now you will be more disappointed by the things that you didn’t do than by the ones you did do. So throw off the bowlines. Sail away from the safe harbor. Catch the trade winds in your sails. Explore. Dream. Discover.''}{-- Mark Twain}

\cenquote{``Success is not what you have\\ but who you are.''}{-- Bo Bennet}


%% \TODO outputs to the page and the terminal.  It is used for
%% reminders of future work, and a convenient way to build a short
%% outline for a sheet in-progress.

Well, this meeting certainly turned out a lot more exciting than you had thought. There's actually a second world and it even has people living in it. This is excellent for the scientists - they can test out their own theories on the convergence. And you can test out your own private theories on it as well. You'll just have to continue it in private as you have been for the last many years. 

Officially, you've been brought along to this meeting to recharge batteries and provide maintenance for the scientists equipment. If nothing else, they do recognize your skill at that here - no doubt you're faster and better at recharging the batteries than anyone else around. They certainly break a lot less often and work better when you do it. Finally you convinced the higher ups (and in particular the Undersecretary of Technology, \cPoliTwo{\intro}) that you were worth bringing along. After years of being passed over because you didn't have a silly degree, you finally earned an official title. But you're certain you're capable of doing more than just charging the batteries  - while that's all you get credit for, it certainly isn't the only thing you plan to do. 

Unfortunately, there's two main scientists here as well though - \cSciOne{\intro}, the senior, and \cSciTwo{\intro}, the junior. Or at least those are their official statuses. \cSciOne{}'s probably got an extra degree or something. They're supposed to be your bosses. In charge of you - doesn't matter that you're older than them and have proved your worth many times over. They've got the fancy degrees, and you're just an old man who happens to be good at stuff. This whole hierarchy is silly - no reason you shouldn't have the most competent person be the one able to do the most useful tasks. 

For the last several years, while the scientists have been working on their convergence theories you've also been working. They don't really think you're content to just sit around and charge batteries, do they? Regardless, having access to all of the supplies and equipment has been excellent for your own research. You think you're nearing a breakthrough - and this alignment of the universes would be the perfect time to test it. The scientists are convinced their research is the path to save the world. You have a slightly different plan - one which they couldn't see with their closed 'educated' minds. You aren't so sure what yours will do, but you think it might be even better than theirs. It certainly seems to have the potential to be more powerful than the weak little portals the scientists have been making. 

Of course, you can't just tell \cSciOne{\informal} and \cSciTwo{\informal} that their work isn't necessarily the right way. They certainly wouldn't be happy with that. And conflict goes against your morals - you've become a pacifist in your older years. After you realized the instabilities with the world and that it was nearing the end, you couldn't bear the thought of intentionally harming anyone. The world seems to be doing a good enough job of that by itself. Especially now that there's a new set of people present. Differing belief systems have led to war in the past, and there just isn't time for this now - not with the imminent end of the world upon you. So your research needs to be done in private and quietly so as to avoid any unwanted conflict. When it works, it will speak for itself. 

To get your research to speak for itself, you will unfortunately have to achieve success in the ways the scientists typically think of though. The best way to do this without hurting anyone is to participate in their publishing race. Whoever accomplishes scientific experiments can put their name on the list. And at the end of the day, the person with the most entries is apparently the best. Can you beat both of them with their fully equipped lab (that you just have to sneak into)? Not likely, but you can at least get yourself on the list. And maybe help the most deserving one win.

Of course, you can advance your agenda of pacifism in more direct ways. Your newest and best method to recharge batteries involves extracting energy from weapons. With as powerful as they make them - seemingly in this magical world in addition to your own world - they can provide a huge amount of energy very quickly. This is definitely better than your standard technical methods. And fortunately it provides a good excuse to destroy weapons to make sure no one harms one another.

Of course, with all this chaos and world ending in place an old \pronoun{\human} like you needs some reassurance. Back in your childhood you used to go to church. Haven't been in a while since religion fell out of style a long time back. But a sermon or two would probably help settle your mind and prepare you for whatever might happen today. 

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Make sure the batteries needed by the scientists remain charged. That is your official job after all - no reason to upset the Undersecretary of Technology by not doing so. 
  \item Finish your own research. You've been working on it for years and need to finish it before you all die. Who knows, maybe it will even give the insight to save you all?
  \item Spread the word of pacifism. Even if the world is ending, we all ought to respect each other.
  \item Find religious comfort. Get to a sermon or two. It will help you deal with all this frustration.
  \item Ensure the system for recognizing people for their actions is fair. Giving people positions just because they've got degrees, money or age is silly. Judgment should be based off your competence and performance. 
\end{itemz}

\begin{itemz}[Notes]
  \item Asking about what degrees or official qualifications you have annoys you. Those aren't what defines your competence. Roleplay accordingly.  
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cSciOne{}} The head scientist on this mission. Officially. 
  \contact{\cSciTwo{}} The subordinate scientist on this mission. Officially. 
  \contact{\cServant{}} Your double. 
\end{contacts}


%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.
\starttag{mems}

  \mTest{}

  \memfold{``Rosebud''}{Rosebud!  That was the name of\ldots the name
  of\ldots darn, you forget.}

  \startmembook{Book of Mempackets}

    \mempage{if you see something blue}{Hey, that's blue!  Oh, you
    remember, blue is your favorite color.  You really like blue
    things, especially blue tentacles.  You wonder why\ldots}

    \mempage{``Octy''}{Octy!  You remember Octy now!  She was your pet
    blue octopus when you were a young child living offshore.  Oh, the
    fun times you had!

    You used to go swimming and diving with Octy all the time.  This
    was years ago.  What happened?  You still can't remember\ldots but
    you know you haven't even thought of her since you were small.}

  \endmembook

\endtag

\starttag{abils}
  \ability{Amazing Powers}{You can do strange and amazing things.}{I
  do something strange and amazing.}
\endtag


\end{document}
