\documentclass[blue]{guildcamp3}
\begin{document}
\name{\bMagicWorld{}}

The world you grew up in is suffused with magic. Over the course of centuries, your people have tamed it and bound it to their will, making your society a tapestry of wonders. There is a working for just about anything, making lives easier in accordance with magical skill. Any individual can incant simple spells to clean house, grow crops, animate vehicles, and communicate mind to mind, allowing people to overcome barriers of culture and language. Coming together for a group working, your people can raise towers, travel instantly, and make uninhabitable wastes suitable for settlement. Through magical scholarship, your people have even managed to extend your society to your planet's moon and beyond. Unity through magic and magic through unity is your mindset, and those who excel in magical scholarship to better the world are held in high esteem. After all, it is mages like them who raised your forefathers from the dark ages of confusion and toil.

In your world, magical skill is a born talent that runs deep in families. The noble families that rule your nations and the prominent lines who most often have contributed to arcane scholarship have attained their rightful place in society because of the strength of magic in their blood, as is rightfully so. Magic is necessary for civilized society, so it makes perfect sense for those who guide society to be those born with the strongest connection to the deep magic. The middle classes are populated by those whose magic is of moderate strength, whose power allows them to perform skilled services, craft valuable products, and do important civic works. The lower classes are those whose magic is more suited to unskilled labors. All in all, every strength of magic plays its proper role in society.

Occasionally, a child is born with no magical skill. As such children can provide no useful contribution to society, they are generally removed from public view or mercifully removed from society, as such lesser beings would live burdensome lives of suffering. Those who have produced such a child generally experience a strong sense of shame. What flaw in their magic could have led them to produce such miserable progeny? Producing offspring whose magic is equal to or greater to their own is an important part of improving society, so it is considered a personal failure, or even a malicious attack, to produce a non-magical child.

In your society, the highest virtues are magical skill, contributing to one's necessary role according to one's class, unity through magic, magic through unity, and ever-increasing your society's level and grasp of the arcane. The lowest vices are lack of magical skill, failure to perform one's necessary role according to one's class, failure to unite for magical betterment, and lowering the level of magic in your society. For this reason, it is vital to give the utmost respect to those whose magical contribution to society is greater than one's own, and to never debase oneself by attacking the foundations of society through eschewing the study of magical betterment or deliberately polluting your class through producing progeny of poor magical pedigree. On the other side of things, the highest praise is awarded to those who are able to commune so closely with the deep magic and the gods that govern it that they can produce magical energy through trance. This is an immensely holy act, and all in your society view the trance with reverence, the sign of utmost holiness and union with the gods.

In your society, participating in religious devotion is seen as vital to the goals of society. Honoring the gods and inviting their favor allows magic to flow and arcane scholarship to make further improvements to your way of life. It is the gods who have blessed your with magical skill. Devotional activities, particularly those performed as a group, are an important way of promoting unity through magic and magic from unity. It is seen as highly detrimental to society to blaspheme the gods or ignore one's metaphysical duties. Such things are an attack on your entire way of life. Atheism is therefore the ultimate taboo in your society, the denial of the gifts of the gods a glob of spittle upon their holy faces. Due to the important role of religion in society, members of the holy orders are always represented in government.

Though there are numerous nations on your home planet, national governments will occasionally come together for the good of your world, forming the Convocation of Nobles to oversee grave issues such as war or plagues. They work closely with the academies of arcane scholarship to come up with solutions to these problems. If necessary, the Convocation can dip into their arsenal of magical weapons. The rulings and actions of the Convocation of Nobles can be harsh, but ultimately you know that it is for the good of your world.

Over the past few months, panic has begun to ripple through the generally peaceful nations, as a series of seemingly inexplicable natural disasters and unusual occurrences have been noted across the globe, speculation spreading like wildfire across the magically-facilitated communication networks. Reports are coming in of entire cities being stripped of their magic, leading to the toppling of towers and deaths by the hundreds from plague, injury, and suicide, what appear to be holes in the sky through which strange visions are visible, and rivers turning to blood. A secret Convocation of Nobles was called together to address these events. Being high-ranking members of the Convocation and those working with them, you know that things are far worse than most citizens know. These phenomena are side effects of the destabilization of the deep magic that is the fabric of your universe. Your mages have made the grave discovery that some unknown force is causing your universe to literally fall apart, and it is only a matter of time before your universe disintegrates altogether.

Luckily these same mages have been able to determine that a nearby universe reachable from your own has a source of energy that will re-stabilize the deep magic, which is why all of you have been brought together at this secret base. Their highly advanced magical powers have led them to work on constructing what they call the Global Friendly Godmother (GFG). Your job is to facilitate connection with this alien universe and acquire the source of energy to save your world before it is too late. Only about four hours remain before destabilization is complete and irreversible.

The current status of operation for magical items is denoted by $\mu$. At game start $\mu$ is zero. Individual members of the \bMagicWorld{} have personal mana storage. The maximum capacity of your personal mana storage is noted on your character sheet with the letter $\alpha$. You start the game with that much mana unless you know otherwise. Certain in game activities may require or give $\alpha$ - in that case increase or decrease your level accordingly. Your maximum capacity always remains as written on your character sheet. 

\begin{itemz}[Goals]
	\item Cooperate amongst your peers and those from the other universe to save the world
\end{itemz}


\begin{members}
	\member{\cNobleOne{}} The Undersecretary of Arcane Research (oddly, \cNobleOne{they} are well-versed in theory but have no innate magical power)
	\member{\cMageOne{}} Head Mage
	\member{\cMageTwo{}} Mage
	\member{\cPaladin{}} Paladin, Representative of the Faith
	\member{\cRogueOne{}} Member of Base Security
	\member{\cRogueTwo{}} Member of Base Security
	\member{\cServant{}} \cNobleOne{}'s Servant
\end{members}

\end{document}
