\documentclass[blue]{guildcamp3}
\begin{document}
\name{\bMagicMob{}}

\bigquote{``The Golden Rule: Those who have the gold, rule''}

You are a member of \bMagicMob{}. This proud organization has long worked from the shadows to build itself up as a subtle but undeniable influence at all levels of \bMagicWorld{} society. Harking from a time when self righteous fools believed they could force their beliefs on consumption onto the rest of society. While quick money brought quick power, those who brought all the criminals together, with blood in some cases, were wise enough to keep excesses to a minimum. The law may be on the lookout for what they can, but in truth the leaders of \bMagicMob{} have been wise enough to spend their wealth in forging connections throughout society deeply enough that being uprooted is impossible. You are simple proof that the fingers of \bMagicMob{} dip into the highest of secrets. Our name is feared, whispered in the night, we are those that have not mercy for the other, the outsider. Oddly enough, we have through connections found another version of ourselves on the other side. Now to make a profit from this. Take care lest the other group, while given incentive to work with you, betrays you. You have your assignments given individually. That is the way so that even under the harshest of enemy interrogation a sibling will not betray. You are allowed to share you mission with other members if necessary, and only if necessary.

Now, one of the main commodities you all deal in around here is, well, rare and highly volatile drugs. Specifically, \iDrugsMagic{}. Worth lots of gold, and it's rumored the occasional person might have tried a dose too many... It's a highly volatile compound, only stable in its special preservation case (which has the convenient side effect of making it difficult to detect). The mob from the other universe deals in drugs as well, and you've been tasked with bringing a sample back to your world. You need to be holding a sample of the drugs-- and any stabilizing equipment it requires-- when the convergence of worlds ends. The mob had you bring in several samples of \iDrugsMagic{} to trade for whatever compound they have on their side.

Given that everything got kind of thrown around in this convergence, you'd better make sure the \iDrugsMagic{} is still in its case, lest it get destroyed (20 minutes out of the case will destroy it. And there's no way you'd get past a police officer with their highly sensitive magic unless it were in the case). Regardless, to get that sweet gold, you'd better find your case before the \bTechMob{} does. 

\begin{itemz}[Goals]
	\item Find out the members of the other side's group
	\item Make the drug exchange. Your drugs and the case are denoted by item number \iDrugsMagic{}.
	\item Do not get caught, if caught your outside connections can only help after the event is done
\end{itemz}

\begin{members}[Official Members]
	\member{\cNobleTwo{\intro}} Your dear governmental leader. Thank goodness \cNobleTwo{\they} are on your side - helps with all the legal issues. 
	\member{\cServant{\intro}} A servant. Who seems to have gotten caught up with the mob for some reason.
		
	\end{members}



\end{document}
