\documentclass[blue]{guildcamp3}
\begin{document}
\name{\bTechMob{}}

\bigquote{``Blood is thicker than water, weighs heavier than gold, binds tigher than anyother loyalty. We are \bTechMob{} and we remain true to ourselves, burn the rest.''}

You are a member of \bTechMob{}. This proud organization has long worked from the shadows to build itself up as a subtle but undeniable influence at all levels of \bTechWorld{} society. Harkening from a time when self-righteous fools believed they could force their beliefs on consumption onto the rest of society. While quick money brought quick power, those who brought all the criminals together, with bloodshed in some cases, were wise enough to keep excesses to a minimum. The law may be on the lookout for what it can find, but in truth the leaders of \bTechMob{} have been wise enough to spend their wealth in forging connections throughout society so deeply that it cannot be uprooted. You are simple proof that the fingers of \bTechMob{} dip into the highest of secrets. Our name is feared, whispered in the night, we are those that have not mercy for the other, the outsider. Oddly enough, we have, through our special connections, found another version of ourselves on the other side. Now to make a profit from this. Take care lest the other group, while given incentive to work with you, betray you. You have your individual assignments. That is the way so that, even under the harshest of enemy interrogation, a sibling will not betray. You are allowed to share your mission with other members if necessary, and only if necessary.

Now, the main commodity you all deal in around here is, well, drugs. Specifically \iDrugsTech{}. Worth lots of money, and it's rumored the occasional person might have tried a dose too many... It's a highly volatile compound, only stable in its special preservation case (which has the convenient side effect of making it difficult to detect). The mob from the other universe deals in drugs as well, and you've been tasked with bringing a sample back to your world. You need to be holding a sample of their drugs-- and any stabilizing equipment it requires-- when the convergence of worlds ends. The mob had you bring in several samples of \iDrugsTech{} to trade for whatever compound they have on their side.

Given that everything got kind of thrown around in this convergence, you'd better make sure the \iDrugsTech{} is still in it's case, lest it get destroyed (20 minutes out of the case will destroy it. And there's no way you'd get past a police officer with their detectors unless it were in the case). Regardless, to get that sweet money, you'd better find your case before the \bMagicMob{} does. 

\begin{itemz}[Goals]
	\item Find out the members of the other side's group
	\item Make the drug exchange. Your drugs are denoted by item number \iDrugsTech{}.
	\item Do not get caught. Your outside connections cannot help you during this event, and they may not be so merciful as to help you afterwards.
\end{itemz}

\begin{members}[Official Members]
	\member{\cSciOne{\intro}} The current leading scientist of \bTechWorld{}. \cSciOne{\They} can probably do just about anything technical you might need in order to accomplish the mob's goals. 
	\member{\cSpecOpTwo{\intro}} The new security guy. Who knows how \cSpecOpTwo{\they} ended up in the mob.

\end{members}



\end{document}
