\documentclass[blue]{guildcamp3}
\begin{document}
\name{\bTechWorld{}}

The world you grew up in stands on the shoulders of giants. Thousands of years of technological and scientific advancement have created a society where machines and medicine make a comfortable life possible for anyone who can afford them. Sparkling cities with cloud-piercing skyscrapers dot your continents, interspersed with plains fruited with the bounty of optimally enhanced crops, hydroponic centers, and factories where cruelty-free meat is grown in vats. Animals raised for their eggs and milk live out their lives in comfort on the tiered green towers that dot the rural areas. Pollution is all but a thing of the past. Your technological predecessors relied on such technology to build up your nations, but in time new technologies made such things obsolete and made it possible to clean the land and air of the pollutants that had been previously released. Your people have even managed to colonize your planet's moon and are ever-expanding towards the stars.

A few decades ago, it became possible to enhance the DNA of zygotes early in a pregnancy to ensure that the potential child would be healthy and intelligent. Now, a few generations later, most citizens have gone through enhancement in the womb, giving them the best chance at success in society. There are some among the poorer classes that cannot afford enhancement for their children, but such children still play a part in society, filling supportive roles to those with a higher potential for innovation and success. Technically it would be possible for an unenhanced citizen to attain a high-level role, but as they are in competition for jobs and school positions with citizens whose intelligence and skills have been genetically enhanced, this is fairly rare, and some would disapprove of the appointment of the unenhanced when there are those who were literally born for such roles.

In your society, the highest virtues are intelligence, innovation, technological skill, wit, and ability to perform one's role well. The lowest vices are, conversely, stupidity, willful ignorance, dullness, lack of technological skill, and failure to perform well in one's role. A high value is placed on striving for perfection. It is accepted that true perfection is impossible, but it is unseemly to make plain one's failures or to rub imperfection in other people's faces. For this reason, those who either willfully stray from the mold by not curing their disabilities or cannot afford the procedure are generally looked upon with distaste. A successful society requires all to strive for perfection and promote community through conforming to the highest standard. A disability is considered any condition that will disallow a person from integrating fully with society or will prevent them from optimal performance in their role. Particularly distrusted are those with disorders of the transient mind, who experience uncontrollable trances during which they cannot work and are unreachable for communication with their peers.

To ensure maximum safety, there are strict regulations on performing scientific experiments. To perform scientific experiments and do research, one must first get a license signed off on by the Undersecretary of Technology. This is not a license given lightly - it is only given to those who prove themselves worthy. Practicing research and experiments without a license is grounds for arrest and possibly even time in prison. In this way, it can be ensured that the path of scientific progression only goes in a positive direction and never strays into the unethical. This goes doubly so for any research on human and animal subjects - nothing must be done to humans without full approval of the government. 

Religion is generally seen as a relic of the primitive past. Though there are some who follow a religious tradition, they generally keep it private because of the taboo nature of religious devotion. Those who have religious faith, especially those who set aside time for prayer and metaphysical activities, are seen as intentionally wasting time that could be spent productively or socially elsewhere. It is also seen as illogical to believe in things that have no scientific evidence to prove they exist, such gods. For this reason, churches generally have no representation in government.

Though there are numerous nations on your home planet, national governments are not the top of the food chain. The Cooperative Plurality of Nations governs international affairs and matters of planet-wide concern. Though its image is presented as peaceful, everyone knows that dissent and war are solved with an iron fist. Its Department of Defense has an arsenal of high-tech weapons almost beyond imagination.

Over the past few months, panic has begun to ripple through the generally peaceful plurality of nations, as a series of seemingly inexplicable natural disasters and unusual occurrences have been noted across the globe, speculation spreading like wildfire across the digital networks. Reports are coming in of cities disappearing off the face of the planet, temperature fluctuations causing lakes to boil and people to freeze solid in their beds, and stars and planets to seem to dance in the sky. Being high-ranking members of the Cooperative Plurality of Nations, you know that much of this information is being suppressed, but somehow some news makes it through uncensored. The truth is much worse than the people know. These phenomena are side effects of the destabilization of space time. Cooperative Plurality scientists have made the grave discovery that some unknown force is causing your universe to literally fall apart, and it is only a matter of time before your universe disintegrates altogether.

Luckily these same scientists have been able to determine that a nearby universe reachable from your own has a source of energy that will re-stabilize the fabric of your universe, which is why all of you have been brought together at this secret research base. Your job is to facilitate connection with this alien universe and acquire the source of energy to save your world before it is too late. The official scientists are hard at work on a machine - they call it the Geospatial Fusion Globemaster (GFG) to help with this. Only about four hours remain before destabilization is complete and irreversible.

The current status of operation for technical items is denoted by $\tau$. At game start $\tau$ is zero. Individual citizens of \bTechWorld{} have personal batteries which can be used to power day to day devices or more elaborate ones. The maximum capacity of your personal battery is noted on your character sheet with the letter $\omega$. You start the game with that much battery level unless you know otherwise. Certain in game activities may require or give $\omega$ - in that case increase or decrease your level accordingly. Your maximum capacity always remains as written on your character sheet. 

\begin{itemz}[Goals]
	\item Cooperate amongst your peers and those from the other universe to save the world
\end{itemz}


\begin{members}
	\member{\cPoliOne{}} The Secretary of Defense
	\member{\cPoliTwo{}} The Undersecretary of Technology
	\member{\cSciOne{}} Head Scientist
	\member{\cSciTwo{}} Scientist
	\member{\cTech{}} Technician
	\member{\cSpecOpOne{}} Member of Base Security
	\member{\cSpecOpTwo{}} Member of Base Security
\end{members}

\end{document}
