%%%%%
%%
%% Notebooks live in this directory.  There are two kinds: in-game
%% notebooks (like classic research notebooks) and out-of-game
%% notebooks (also known as green notebooks).  Both kinds are defined
%% in Lists/notebook-LIST.tex.  In-game notebooks, defined as Notebook
%% macros, get assigned in \MYitems.  Out-of-game notebooks, defined
%% as GreenNotebook macros, get assigned in \MYgreens.
%%
%% This file doubles as a latex'able example out-of-game notebook.
%% README.tex, also in this directory, doubles as an example in-game
%% notebook.
%%
%% Notebook and GreenNotebook macros each have a file that lives here.
%% The argument to \startnotebook{...}  probably should be the macro
%% for the given notebook.  However, you can also just use
%% \startnotebook{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%
%% If you want to use notebooks for memory packets, see related macros
%% in Lists/mem-LIST.tex (and in Charsheets/README.tex).  If you want
%% more programmatic control over the structure/linkage of notebooks,
%% like for a computer security mechanic, see LabelCover and LabelPage
%% in Lists/sign-LIST.tex.
%%
%%%%%

\documentclass[greennotebook]{guildcamp3} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nEscapePodMagic{}}

% this belongs to rogue 1 and can hold only one person
% final parts needed: sheet of scrap metal (page two), belladonna syrup (page five), stardust (page three), dragon skin (page six), unicorn hoof (page seven), werewolf fang (page four), and holy water (page five)

%% The argument to \begin{page}{...} is a reference string.  You use
%% \nbref{...} in page text to refer to a given page.  These
%% references will be typeset as numbers, based on the order of the
%% pages.
\begin{page}{first}

Well, given that your double is apparently worthless enough to have gotten removed from the other universe you certainly don't want to end up \emph{there}. Who knows if it's even worth living in your own world? Regardless, you aren't so certain those mages know how to save the world or anything so you'd best take matters into your own hands. You've read about a way to escape to another world entirely, maybe that'd be for the best. Do you care if other people know you want to escape? Probably not - not like anyone cares about you anyway.

You know, your own universe ending would be a pretty terrible thing to have happen. Better not go any further in this escape pod effort until you've found the three items needed to find the artifact order. Once you've figured out what those three items are, you can turn to \nbref{magicpagetwo}.
\end{page}



%% the optional argument [One Minute] means this page will be labeled and
%% referenced with a string instead of a number.  The numbering of other
%% pages will ignore this one.
\begin{page}[that's done]{magicpagetwo}

Now you can figure out the artifact order. Great. And you know you need a sheet of \iScrapMetal{} to build an escape pod. Wow, what a surprise. Good thing there's a lot of that around here. 

Well, now that that's out of the way maybe you should figure out what happened to your double. Once you've figured that out you can turn to page \nbref{magicpagethree}

\end{page}

\begin{page}[oh my...]{magicpagethree}
	
Well, that's horrible. You can't even believe it. Better find a universe where you don't have to see anyone like that ever again. At least you figured out you'll need a jar of \iStardust{} in order to build an escape pod. Why? Who knows? But at least you'll have it. 

You know, practicing your poetry would be a good idea. Maybe writing a limerick would do you good. Learn enough about the tech world to write a limerick about it, and then perform that limerick in front of at least three people. Once you've done that turn to page \nbref{magicpagefour}

Note: a limerick consists of 5 lines. The first, fourth and fifth line have seven syllables and must rhyme with each other. The second and third lines have five syllables and rhyme with each other. 
	
\end{page}

\begin{page}[poetry is nice]{magicpagefour}
	
Well, that poem gave you inspiration. Pretty sure you need a \iWerewolfFang{} and some \iHolyWater{} to build an escape pod.  

Better make sure the world is saved. Once the machine has been run to determine the artifacts needed to save the Magical World you can turn to \nbref{magicpagefive}.
	
\end{page}

\begin{page}[ok, it ran...]{magicpagefive}
	
The machine ran. And in it's running it let you know you'd need \iBelladonna{} to build an escape pod. Why on earth it you'd need that you have no clue...

This is all rather confusing. See if you can attend a sermon to clear your mind. Once you've attended a sermon, then turn to \nbref{magicpagesix}.
	
\end{page}

\begin{page}[alleluia!]{magicpagesix}
	
Well, the sermon wasn't as inspiring as you'd hoped. You lose one unit of $\alpha$ But you did get a flash of divine inspiration. You'll need some \iDragonSkin{} to build this escape pod. Finally an ingredient that makes sense - wouldn't want the pod to rip apart. 

You are feeling a bit weak after this. See if you can get your $\alpha$ back up to 2 before you continue this. Once you do, turn to page \nbref{magicpageseven}
	
\end{page}

\begin{page}[that's better]{magicpageseven}
	Well, now you know you'll need a \iUnicornHoof{} too for this machine. Too bad you lose another $\alpha$ trying this. 	
	
	Well, you know all the parts you need to build it. Now you've just got to find them all. Find all of the parts and spend seven minutes working with them and a cauldron (\iCauldron{}) at a ritual desk. Once you've done that you can turn to page \nbref{last}. 
	
	Note: the needed parts were: \iUnicornHoof{}, \iDragonSkin{}, \iBelladonna{}, \iHolyWater{}, \iWerewolfFang{}, \iStardust{}, and \iScrapMetal{}. 
\end{page}

\begin{page}[you've done it]{last}

Destroy the items needed for building the escape pod other than the \iCauldron{}. At least something has gone your way today. 

Your escape pod is created. It's a small pod, only big enough for you. If you want to escape to a random third universe, then sign your name below and ensure you have at least two units of $\alpha$ at game time T+4:00. 

Name:............................................................

\end{page}



\endnotebook

\end{document}
