\documentclass[greennotebook]{guildcamp3} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nTechBubble{}}

% this belongs to 
% parts needed: sheet of scrap metal (page 1), flashlight (page 4), circuit board (page two), graphite lube (page three), cog (page two), transistor (page six), niobium carbide (page 5) - use a screwdriver


%% The argument to \begin{page}{...} is a reference string.  You use
%% \nbref{...} in page text to refer to a given page.  These
%% references will be typeset as numbers, based on the order of the
%% pages.
\begin{page}{first}
	
With the discovery of this new Magical World, it certainly would be nice if your technical objects could still function over there.  

Follow the instructions in this notebook to build a bubble that allows technical items to use magical energy instead of an internal battery. 

Well, your official job here is to find a way to not let the worlds end. After all, if they do you won't be able to use Tech anywhere. Turn to the \nbref{techpageone} after the official speech's at T+1:00 have happened.  

\end{page}



%% the optional argument [One Minute] means this page will be labeled and
%% referenced with a string instead of a number.  The numbering of other
%% pages will ignore this one.
\begin{page}[The proposal is finally done...]{techpageone}

Thank goodness that piece of paperwork is finished. And for some strange reason, you were told a sheet of \iScrapMetal{} will be needed for a bubble. In all likelihood some of the other parts needed for the machine are probably useful for a bubble too. Once the scientist's machine has been built turn to \nbref{techpagetwo}.

\end{page}

\begin{page}[And some of those things really are useful]{techpagetwo}
	
Well, a \iCircuitBoard{} and a \iCog{} are useful for bubbles as well. 

All this science makes your head spin. You'd kind of like some reassurance. When you attend a religious ceremony for two minutes, you can continue to \nbref{techpagethree}. 
	
\end{page}

\begin{page}[good...]{techpagethree}
	
Much better. Making sure the bubble runs smoothly in a non-technical world might be difficult - some \iGraphiteLube{} will help with that. 

Other things that might help let Technical items function in a Magical World? You're not so sure about those. Maybe if you got some intelligence on the Magical world that would help you figure this out. 

Spend at least two minutes talking to at least two different people with magical abilities (one of whom must be some sort of security person). After you do so, you can turn to \nbref{techpagefour}

\end{page}

\begin{page}[all that magical thought...]{techpagefour}
	
Well, that was mildly useful - a \iFlashlight{} might help somehow. Some money might help in building this machine... Turn to \nbref{techpagefive} after you've acquired an additional 10 gold (not including the gold you started with...).
	
\end{page}

\begin{page}[money is always useful]{techpagefive}

You did always like money. And what can money buy? Apparently \iNiobiumCarbide{} which you can also use to build a bubble. Unfortunately all this distraction has lowered your current $\omega$ by one. That's really annoying. Maybe you'd feel better if someone else felt similarly...

Once you make two people become embarrassed you can turn to  \nbref{techpagesix}.

\emph{out-of-game: their characters of course. Just be honest here.}
	
\end{page}

\begin{page}[that did help]{techpagesix}
	
Well, you don't feel any worse now. And you've learned that the last item you need to build a bubble is a \iTransistor{}. 

Well, now you've got to build this silly bubble. You'll need to gather all the pieces needed and use a \iScrewdriver{}. Really. You. A politician. Use a screwdriver. You must work on them with the screwdriver for five uninterrupted minutes. Once you've done so, you may turn to page \nbref{last}. This will also consume one unit of $\omega$.

As a reminder, the items needed were: \iScrapMetal{}, \iCircuitBoard{}, \iCog{}, \iGraphiteLube{}, \iFlashlight{}, \iNiobiumCarbide{}, and \iTransistor{}. 
	
\end{page}	


\begin{page}[at last...]{last}
	
Destroy the items needed for building the bubble other than the \iScrewdriver{}.

Your bubble has been created. Hooray! Now any items which you are using that would normally require $\omega$ can use either $\omega$ or $\alpha$ scores interchangeably. Your tech will work in the other world! At least as well as it does at home... 

Show anyone who believes you cannot do this, this page as proof. This page is out of game. In game, their character just sees the item work. 


\end{page}



\endnotebook

\end{document}
