\documentclass[greennotebook]{guildcamp3} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nTechWorldSave{}}

\begin{page}{TechWorldSaveFirst}
	
Just because you were not able to get that little pathetic piece of paper saying you are qualified, does not mean you are incapable of research. You have some of your own research to finish, the work of years that seems to be so close to a breakthrough. Just do not let the scientists stop you or catch you.  

To study an item hold or touch it openly treating it as though it were one hand more bulky than it is. 

First you need to get a hold of a \iCircuitBoard{} and study it for 5 minutes, this does not consume the item. Once done turn to \nbref{TechWorldSaveSecond}
	
\end{page}

\begin{page}{TechWorldSaveSecond}
	
Next you need to get a hold of a \iMagnet{} for and leave it next to your \sTechWorkbench{} for 10 minutes for calibrations to be run, you do not need to stay there while it is being measured. Once done turn to \nbref{TechWorldSaveThird}

	
\end{page}

\begin{page}{TechWorldSaveThird}
	
Now get a \iLeadPipe{} and measure the magnetic resonance with the \iMagnet{} for 1 minute seconds uninterrupted this will require you to have one person hold the \iLeadPipe{} and another hold the \iMagnet{} they cannot be one of the scientists. Once done turn to \nbref{TechWorldSaveFourth}
	
\end{page}

\begin{page}{TechWorldSaveFourth}
	
	Things are making more sense now. You need to go grab a piece of \iScrapMetal{}, there should be plenty around, and take it back to your \sTechWorkbench{}. Then turn to \nbref{TechWorldSaveFifth}
	
\end{page}

\begin{page}{TechWorldSaveFifth}
	
	Getting closer, next you need to grab a \iMonoBlade{} to take samples from the \iScrapMetal{} at your \sTechWorkbench{}, though not enough to consume the \iScrapMetal{}, the process will take 1 minute  afterward turn to  \nbref{TechWorldSaveSixth}
	
\end{page}

\begin{page}{TechWorldSaveSixth}
	
	 Got to go find a  \iSieve{} to help filter your scrapings and mix with a little \iBloodPlasma{} though not enough to consume it, this will take 3 minutes at your \sTechWorkbench{}, then turn to  \nbref{TechWorldSaveSeventh}
	
\end{page}

\begin{page}{TechWorldSaveSeventh}
	
	So close you can almost taste the breakthrough, now you just need a \iCentrifuge{} to separate your samples out, this will take 12 minutes as long as no body moves the \iCentrifuge{} you do not need to be present though you will need just a little \iGraphiteLube{} though not enough to consume it. Then turn to  \nbref{TechWorldSaveEighth}
	
\end{page}

\begin{page}{TechWorldSaveEighth}
	
	 You have it, you need to go to your \sTechWorkbench{} with the following items: 3 \iTFResistor{}s, \iScrapMetal{}, \iCog{}, \iCircuitBoard{}, \iFlashlight{}, \iMultitool{}. Then work on them for 5 minutes you will need someone to hold the \iTFResistor{}s, another to hold  \iScrapMetal{} a third to hold the \iCog{} and a fourth to hold the \iCircuitBoard{} while you hold the \iFlashlight{} and \iMultitool{}, once this has happened, consuming items that are labeled consume on use, turn to \nbref{TechWorldSaveNineth}.
	
\end{page}

\begin{page}{TechWorldSaveNineth}
	
	You have it, it works, and you have a slight headache as ideas, concepts never thought of run through your mind. You have a way to increase your value for the end of game mechanic from 1 to 2.  You must gather 3 pairs of doubles and all get together and hold hands in a circle with each of you across from your double. In the middle of the circle, you must place two vials of \iBloodPlasma{} and one \iEctoplasm{} on top of two dead bodies - one from each world. You must remain this way for at least 3 minutes within visual range of the artifacts during the last 15 minutes of game (after T+3:45). 
	
\end{page}

\endnotebook

\end{document}


%Once done turn to the \nbref{TechWorldSaveSecond}
