%%%%%
%%
%% This file sets up the Abil datatype and creates Abil macros.  These
%% are for abilities that characters may have.
%%
%%%%%

\DECLARESUBTYPE{Abil}{Element}
\PRESETS{Abil}{
  \F\MYtext	%% text of ability, read by user
  \F\MYeffect	%% effect text of ability, read by recipient(s)
  }


%%%%%
%% \ability{<name>}{<text>}{<effect>}
%%
%% \ability is a wrapper around \INSTANCE, useful for 1-shot abilities,
%% etc.
\newinstance{Abil}{\ability[3]}{
  \s\MYname{#1}\s\MYtext{#2}\s\MYeffect{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Abil}{\aTest}{
  \s\MYname	{Test Ability}
  \s\MYtext	{You are a test.}
  \s\MYeffect	{This is a Test.}
  }


\NEW{Abil}{\aFiremansCarry}{
  \s\MYname	{Fireman's Carry}
  \s\MYtext	{You can carry a body as if it were two hands bulky.}
  \s\MYeffect	{I can carry this body well.}
  }
  
  \NEW{Abil}{\aManaDrain}{
  	\s\MYname	{Mana Drain}
  	\s\MYtext	{You drain one unit of mana from a magical person. Your mana level increases by one.}
  	\s\MYeffect	{You feel a chill in your body as your mana level decreases by 1.}
  }
  
  \NEW{Abil}{\aArmoryDoorTech}{
  	\s\MYname	{Open the armory door - tech}
  	\s\MYtext	{You can walk freely through the technical armory door whenever $\tau$ non-zero.}
  	\s\MYeffect	{You see me walk through the armory door.}
  }
  
  \NEW{Abil}{\aArmoryDoorMagic}{
    	\s\MYname	{Open the armory door - magic}
    	\s\MYtext	{You can walk freely through the magical armory door whenever $\mu$is non-zero.}
    	\s\MYeffect	{You see me walk through the armory door.}
    }
    
    \NEW{Abil}{\aSellSecrets}{
    	\s\MYname	{Sell Secrets}
    	\s\MYtext	{You can sell verifiable secrets. The items count as these secrets. To sell them, barter with the person you are selling to and exchange the item card for something.}
    	\s\MYeffect	{You receive a verifiably true secret.}
    	\s\MYitems {\iSecretOne{}\iSecretTwo{}\iSecretThree{}\iSecretFour{}\iSecretFive{}%\iSecretSix{}
	\iSecretSeven{}\iSecretEight{}\iSecretNine{}\iSecretTen{}\iSecretEleven{}\iSecretTwelve{}\iSecretThirteen{}\iSecretFourteen{}}
    }
    
    \NEW{Abil}{\aTruthTelling}{
    	\s\MYname	{Hear Confession}
    	\s\MYtext	{You can compell someone to answer one yes or no questions. This consumes 1 mana. You have 1 use of this ability per person}
    	\s\MYeffect	{You must correctly answer one yes or no question.}
    }   
    
    \NEW{Abil}{\aTrance}{
    	\s\MYname	{Trance}
    	\s\MYtext	{When you do this, remain in a trance for 5 minutes. During this time do not interact with anyone or anything except to show them this card. Appear dazed and disoriented.}
    	\s\MYeffect	{This person appears to be in a sort of trance.}
    } 
  


%% Basic DarkWater-style Martial Attack abilities


%% Everyone has these 3
\NEW{Abil}{\aAssist}{
  \s\MYname	{Assist}
  \s\MYtext	{You can assist someone else's attack.  You must be
		within ZoC of both the attacker and target.  Within two
		seconds of an attack, direct this at the attacker,
		saying ``\MYname'' and your CR.}
  \s\MYeffect	{I assist your attack.}
  }

\NEW{Abil}{\aKnockOut}{
  \s\MYname	{Knock Out}
  \s\MYtext	{You can knock someone out as an attack.  This requires
		a {\bf blunt} weapon.  Say ``\MYname'' and your CR.}
  \s\MYeffect	{I knock you out.}
  }

\NEW{Abil}{\aWound}{
  \s\MYname	{Wound}
  \s\MYtext	{You can wound someone as an attack.  This requires an
		{\bf edged} weapon, such as a knife.  Say ``\MYname'' and
		your CR.}
  \s\MYeffect	{I wound you.}
  }


%% the \basecombat macro can be prepended to the Char abils list
%% (in char-LIST.tex)
\def\basecombat{\aKnockOut{}\aWound{}\aAssist{}}


%% only some people have these
\NEW{Abil}{\aDisarm}{
  \s\MYname	{Disarm}
  \s\MYtext	{You can disarm one item from someone as an attack.  Say
		``\MYname'' and your CR.  Point at the item you want to
		disarm.  If the attack works, they must drop that item.}
  \s\MYeffect	{I disarm that item.}
  }

\NEW{Abil}{\aRestrain}{
  \s\MYname	{Restrain}
  \s\MYtext	{You can restrain someone as an attack.  Say ``\MYname''
		and your CR.  You may freely drag, attack, or (if you have
		a weapon) killing-blow them.  To do anything else, or if
		your health state changes, incant ``release'' and let them
		go.}
  \s\MYeffect	{I restrain you.  You are restrained until I incant
		``release.''}
  }

\NEW{Abil}{\aThrow}{
  \s\MYname	{Throw}
  \s\MYtext	{You can throw someone as an attack.  Say ``\MYname'' and
		your CR.  Point in the direction you want to throw them.}
  \s\MYeffect	{I throw you.  Go in the direction I point ten full steps
		or until you hit a wall or similar.}
  }
  
  \NEW{Abil}{\aPickpocket}{
  \s\MYname	{Pickpocket}
  \s\MYtext	{You may place a sticker on someone once every 2 minutes. Once you have placed three stickers on someone go to a GM and tell them an item you wish to pickpocket from the player. The GM will go to the player and check if they have the item, if the person does the GM will get it from them, if not the GM will get a random item from the person. If someone sees the sticker being placed or points out the sticker being being placed that sticker does not count and you must tell the person what they see.}
  \s\MYeffect	{...}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\NEW{Abil}{\aAnotherTest}{
  \s\MYname	{test}
  \s\MYtext	{test}
  \s\MYeffect	{test}
  }
