%%%%%
%%
%% This file creates the Item, ItemPacket, ItemFold, ItemEnvelope, and
%% ItemLabel datatypes, and creates macros for each.  These are for
%% various types of in-game items.
%%
%%%%%


%%%%%
%% Item macros are for normal item cards.
\DECLARESUBTYPE{Item}{TransElement}
\PRESETS{Item}{
  \FD\MYtext	{} %% longer text of item
  \FD\MYmark	{} %% possible contents of shaded ``mark'' on card
  \FD\MYbulky	{0} %% potential bulkiness
  \FD\MYcapacity{N/A} %% potential capacity
  \sd\MYlistmap	{\item\MYname\ifx\MYnumber\empty\else\ (\MYnumber)\fi}
  }

%%%%%
%% \prop
%% \unstash
%% \bulky{<number>}
%% \contain{<number>}
%%
%% \prop inside an Item macro labels the card as a prop.  \unstash
%% labels the card as unstashable.  \bulky{n} labels the card as
%% n-hands bulky.  \contain{n} labels the card with n-hands capacity.
\def\prop{%
  \append\MYmark{ ~PROP~ }}
\def\unstash{%
  \append\MYmark{ ~UNSTASHABLE~ }}
\def\bulky#1{%
  \s\MYbulky{#1}%
  \append\MYmark{\mbox{ ~\MYbulky-Hand~Bulky~ }}}
\def\contain#1{%
  \s\MYcapacity{#1}%
  \append\MYmark{\mbox{ ~\MYcapacity-Hand~Capacity~ }}}


%%%%%
%% ItemPacket macros are for item cards with an attached packet.
%% They are a subtype of Item.
\DECLARESUBTYPE{ItemPacket}{Item}
\PRESETS{ItemPacket}{
  \F\MYcontents
  }


%%%%%
%% ItemFold macros are for items represented by just a folded packet.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemFold}{ItemPacket}
\PRESETS{ItemFold}{
  \s\MYmark{}
  }


%%%%%
%% ItemEnvelope macros are for items represented by just an envelope.
%% They are a subtype of ItemPacket, with the longer text and ``mark''
%% left blank, since they have no actual item card.
\DECLARESUBTYPE{ItemEnvelope}{ItemPacket}
\PRESETS{ItemEnvelope}{
  \s\MYmark{}
  }


%%%%%
%% ItemLabel macros are for small labels that would get used on
%% physreps, e.g. gun labels.  The ``mark'' is left blank, since
%% it isn't used for these.
\DECLARESUBTYPE{ItemLabel}{Item}
\PRESETS{ItemLabel}{
  \s\MYmark{}
  }


%%%%%
%% \icard[<extras>]{<name>}{<number>}{<text>}
%% \specialicard[<extras>]{<name>}{<number>}{<text>}{<mark>}
%% \itempacket[<extras>]{<name>}{<number>}{<text>}{<mark>}{<contents>}
%% \itemfold{<name>}{<number>}{<text>}{<contents>}
%% \itemenvelope{<name>}{<number>}{<text>}{<contents>}
%% \itemlabel{<name>}{<number>}{<text>}
%%
%% These are wrappers around \INSTANCE, useful for 1-shots.
%%
%% For \icard, \specialicard, and \itempacket, the optional <extras>
%% (in []'s) is for things like \unstash and \bulky{3}.  For example,
%% \icard[\prop\contain{2}]{..}{..}{..}{..} gives an item that has a
%% prop and 3-hands capacity.
%%
%% The last arg (#5) to \specialicard is for anything extra you may
%% want in the ``mark''
\newinstance{Item}{\icard[4][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}#1}
\newinstance{Item}{\specialicard[5][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}#1}
\newinstance{ItemPacket}{\itempacket[6][]}{
  \s\MYname{#2}\s\MYnumber{#3}\s\MYtext{#4}\s\MYmark{#5}\s\MYcontents{#6}#1}
\newinstance{ItemFold}{\itemfold[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemEnvelope}{\itemenvelope[4]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}\s\MYcontents{#4}}
\newinstance{ItemLabel}{\itemlabel[3]}{
  \s\MYname{#1}\s\MYnumber{#2}\s\MYtext{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Item}{\iTest}{
  \s\MYname	{Test Item}
  \s\MYnumber	{0000}
  \s\MYtext	{A Test Item Card}
  }

\NEW{Item}{\iScrewdriver}{
	\s\MYname	{Screwdriver}
	\s\MYnumber	{10001}
	\s\MYtext	{A nice screwdriver.}
}

\NEW{Item}{\iMultitool}{
	\s\MYname	{Multitool}
	\s\MYnumber	{10002}
	\s\MYtext	{A very useful multitool.}
}

\NEW{Item}{\iCauldron}{
	\s\MYname	{Cauldron}
	\s\MYnumber	{10003}
	\s\MYbulky {1}
	\s\MYtext	{A cast-iron cauldron.}
}

\NEW{Item}{\iPlumbicRod}{
	\s\MYname	{Plumbic Rod}
	\s\MYnumber	{10004}
	\s\MYbulky {1}
	\s\MYtext	{A solid leaden rod.}
}

\NEW{Item}{\iMortarPestle}{
	\s\MYname	{Mortar and Pestle}
	\s\MYnumber	{10005}
	\s\MYtext	{A mortar and pestle for grinding ingredients.}
}

\NEW{Item}{\iQuartz}{
	\s\MYname	{Quartz}
	\s\MYnumber	{10006}
	\s\MYtext	{A fist-sized chunck of rose quartz.}
}

\NEW{Item}{\iDiamondDrill}{
	\s\MYname	{Diamond Drill}
	\s\MYnumber	{10007}
	\s\MYtext	{This durable drill has a diamond tipped bit.}
}

\NEW{Item}{\iVial}{
	\s\MYname	{Vial}
	\s\MYnumber	{10008}
	\s\MYtext	{A slender glass vial.}
}

\NEW{Item}{\iCentrifuge}{
	\s\MYname	{Centrifuge}
	\s\MYnumber	{10009}
	\s\MYbulky {2}
	\s\MYtext	{A machine that rotates rapidly to separate liquids of varying densities.}
}

\NEW{Item}{\iTestTube}{
	\s\MYname	{Test Tube}
	\s\MYnumber	{10010}
	\s\MYtext	{A standard glass test tube.}
}

\NEW{Item}{\iCursedTome}{
	\s\MYname	{Cursed Tome}
	\s\MYnumber	{10011}
	\s\MYtext	{This thick, dusty tome has a dark aura surrounding it.}
}

\NEW{Item}{\iLeadPipe}{
	\s\MYname	{Lead Pipe}
	\s\MYnumber	{10012}
	\s\MYbulky {1}
	\s\MYtext	{A heavy lead pipe.}
}

\NEW{Item}{\iSieve}{
	\s\MYname	{Sieve}
	\s\MYnumber	{10013}
	\s\MYtext	{A sieve for filtering solid matter from a liquid.}
}

\NEW{Item}{\iMonoBlade}{
	\s\MYname	{Monomolecular Blade}
	\s\MYnumber	{10014}
	\s\MYtext	{This blade has an edge so sharp it is only one molecule wide at its tip. It almost hurts to look at the edge.}
}

\NEW{Item}{\iGlassLens}{
	\s\MYname	{Glass Lens}
	\s\MYnumber	{10015}
	\s\MYtext	{A precise glass lens.}
}

\NEW{Item}{\iClover}{
	\s\MYname	{Lucky Clover}
	\s\MYnumber	{10016}
	\s\MYtext	{A clover with four leaves coated in a thin layer of gold.}
}

\NEW{Item}{\iMagnet}{
	\s\MYname	{Magnet}
	\s\MYnumber	{10017}
	\s\MYtext	{A fist-sized magnet.}
}

\NEW{Item}{\iPixieWings}{
	\s\MYname	{Pixie Wings}
	\s\MYnumber	{10018}
	\s\MYtext	{A pair of wings harvested from a rare species of pixie. Consume when used.}
}

\NEW{Item}{\iScrapMetal}{
	\s\MYname	{Scrap Metal}
	\s\MYnumber	{10019}
	\s\MYtext	{A hunk of scrap metal. Consume when used.}
}

\NEW{Item}{\iWerewolfFang}{
	\s\MYname	{Werewolf Fang}
	\s\MYnumber	{10019}
	\s\MYtext	{A fang removed from a werewolf during the full moon. Consume when used.}
}

\NEW{Item}{\iEctoplasm}{
	\s\MYname	{Vial of Ectoplasm}
	\s\MYnumber	{10020}
	\s\MYtext	{A stoppered vial filled with ghostly essence. Consume when used.}
}

\NEW{Item}{\iSoulGem}{
	\s\MYname	{Soul Gem}
	\s\MYnumber	{10021}
	\s\MYtext	{This many-faceted gem is massive and pulsing with inscrutable energy. Consume when used.}
}

\NEW{Item}{\iCircuitBoard}{
	\s\MYname	{Circuit Board}
	\s\MYnumber	{10022}
	\s\MYtext	{A circuit board. Consume when used.}
}

\NEW{Item}{\iTFResistor}{
	\s\MYname	{25 Ohm Resistor}
	\s\MYnumber	{10023}
	\s\MYtext	{A 25 Ohm resistor. Consume when used.}
}

\NEW{Item}{\iHResistor}{
	\s\MYname	{100 Ohm Resistor}
	\s\MYnumber	{10024}
	\s\MYtext	{A 100 Ohm resistor. Consume when used.}
}

\NEW{Item}{\iCog}{
	\s\MYname	{Cog}
	\s\MYnumber	{10025}
	\s\MYbulky {1}
	\s\MYtext	{A large cog. Consume when used.}
}

\NEW{Item}{\iSteamTurbine}{
	\s\MYname	{Steam Turbine}
	\s\MYnumber	{10026}
	\s\MYtext	{A massive steam turbine. Consume when used.}
}

\NEW{Item}{\iStardust}{
	\s\MYname	{Stardust}
	\s\MYnumber	{10027}
	\s\MYtext	{A pouch of sparkling stardust. Consume when used.}
}

\NEW{Item}{\iKitsunePelt}{
	\s\MYname	{Kitsune Pelt}
	\s\MYnumber	{10028}
	\s\MYtext	{A flame-red pelt from a fox demon. Consume when used.}
}

\NEW{Item}{\iHolyWater}{
	\s\MYname	{Holy Water}
	\s\MYnumber	{10029}
	\s\MYtext	{A small vial of holy water. Consume when used.}
}

\NEW{Item}{\iBloodPlasma}{
	\s\MYname	{Blood Plasma}
	\s\MYnumber	{10030}
	\s\MYtext	{A small stoppered test tube filled with blood plasma. Consume when used.}
}

\NEW{Item}{\iFlashlight}{
	\s\MYname	{Flashlight}
	\s\MYnumber	{10031}
	\s\MYtext	{A handheld flashlight. Consume when used.}
}

\NEW{Item}{\iFishingNet}{
	\s\MYname	{Fishing Net}
	\s\MYnumber	{10032}
	\s\MYbulky {1}
	\s\MYtext	{A fishing net. Consume when used.}
}

\NEW{Item}{\iTransistor}{
	\s\MYname	{Transistor}
	\s\MYnumber	{10033}
	\s\MYtext	{A small transistor. Consume when used.}
}

\NEW{Item}{\iBelladonna}{
	\s\MYname	{Belladonna Syrup}
	\s\MYnumber	{10034}
	\s\MYtext	{A small stoppered vial of deep purple belladonna syrup. Consume when used.}
}

\NEW{Item}{\iDragonSkin}{
	\s\MYname	{Dragon Skin}
	\s\MYnumber	{10035}
	\s\MYbulky {1}
	\s\MYtext	{A thick patch of dragon skin covered in sparkling scales. Consume when used.}
}

\NEW{Item}{\iUnicornHoof}{
	\s\MYname	{Unicorn Hoof}
	\s\MYnumber	{10036}
	\s\MYtext	{A unicorn hoof, sans horseshoe. Consume when used.}
}

\NEW{Item}{\iSalamander}{
	\s\MYname	{Dried Salamander}
	\s\MYnumber	{10037}
	\s\MYtext	{A dried fire salamander, intact. Highly flammable. Consume when used.}
}

\NEW{Item}{\iGraphiteLube}{
	\s\MYname	{Graphite Lube}
	\s\MYnumber	{10038}
	\s\MYtext	{A tube of graphite-based lubricant. Consume when used.}
}

\NEW{Item}{\iNiobiumCarbide}{
	\s\MYname	{Niobium Carbide}
	\s\MYnumber	{10039}
	\s\MYtext	{A container of niobium carbide, an ultra-hard ceramic powder. Consume when used.}
}

\NEW{Item}{\iPhoenixFeather}{
	\s\MYname	{Phoenix Feather}
	\s\MYnumber	{10040}
	\s\MYbulky {1}
	\s\MYtext	{A large golden phoenix feather. Consume when used.}
}

\NEW{Item}{\iPenicillin}{
	\s\MYname	{Penicillin}
	\s\MYnumber	{10041}
	\s\MYtext	{A bottle of penicillin caplets. Consume when used.}
}

\NEW{Item}{\iCompoundNine}{
	\s\MYname	{Compound 9}
	\s\MYnumber	{10042}
	\s\MYtext	{A stoppered test tube filled with a fluorescent green liquid. Consume when used.}
}

\NEW{Item}{\iOil}{
	\s\MYname	{Oil}
	\s\MYnumber	{10043}
	\s\MYtext	{A bottle of motor oil. Consume when used.}
}

\NEW{Item}{\iWoolofBat}{
	\s\MYname	{Wool of Bat}
	\s\MYnumber	{10044}
	\s\MYtext	{A pouch of wooly hairs from the wings of a vampire bat. Consume when used.}
}

\NEW{Item}{\iZirconia}{
	\s\MYname	{Partially Stabilized Zirconia}
	\s\MYnumber	{10045}
	\s\MYtext	{A fist-sized chunk of zirconia. Caution should be taken since it is only partially stabilized. Consume when used.}
}

\NEW{Item}{\iGraphene}{
	\s\MYname	{Graphene}
	\s\MYnumber	{10046}
	\s\MYtext	{A sheet of single atom thick carbon lattice. Consume when used.}
}

\NEW{Item}{\iDibella}{
	\s\MYname	{Bust of Dibella}
	\s\MYnumber	{10047}
	\s\MYtext	{A bust of Dibella, goddess of beauty and sexual desire.}
}

\NEW{Item}{\iDrugsTech}{
	\s\MYname	{Box of Drugs}
	\s\MYnumber	{10048}
	\s\MYtext	{A box filled with pouches of white powder. Consuming the powder gives a powerful high and hallucinations.}
}

\NEW{Item}{\iDrugsMagic}{
	\s\MYname	{Box of Drugs}
	\s\MYnumber	{10049}
	\s\MYtext	{A box filled with pouches of white powder. Consuming the powder gives a powerful high and hallucinations.}
}

\NEW{Item}{\iTranceCure}{
	\s\MYname	{Trancing Cure}
	\s\MYnumber	{10050}
	\s\MYtext	{A stoppered vial of orange liquid. Consumption of this liquid will render on unable to enter a trance state. Consume when used.}
}

\NEW{Item}{\iMagicArtifactOne}{
	\s\MYname	{Magical Artifact 1}
	\s\MYnumber	{10051}
	\s\MYtext	{An enigmatic, glowing object with too many angles. You cannot tell what color it is. Looking at it for too long causes hallucinations. Indestructible.}
}

\NEW{Item}{\iMagicArtifactTwo}{
	\s\MYname	{Magical Artifact 2}
	\s\MYnumber	{10052}
	\s\MYtext	{A strange, glowing statue that is simultaneously here and not here. Looking at it for too long makes you hear the music of the celestial spheres. Indestructible.}
}

\NEW{Item}{\iMagicArtifactThree}{
	\s\MYname	{Magical Artifact 3}
	\s\MYnumber	{10053}
	\s\MYtext	{A strange, floating purple cube glowing with the opposite of light. Looking at it for too long will give you terrible nightnares. Indestructible.}
}

\NEW{Item}{\iTechArtifactOne}{
	\s\MYname	{Technological Artifact 1}
	\s\MYnumber	{10054}
	\s\MYtext	{A strange mechanical artifact that projects a strong magnetic field. Staying next to it for too long will give you a headache. Indestructible.}
}

\NEW{Item}{\iTechArtifactTwo}{
	\s\MYname	{Technological Artifact 2}
	\s\MYnumber	{10055}
	\s\MYtext	{A large, white, seemingly perfect sphere that produces holograms of your deepest desires. Looking at it for too long will give you a strong sense of melancholy. Indestructible.}
}

\NEW{Item}{\iTechArtifactThree}{
	\s\MYname	{Technological Artifact 3}
	\s\MYnumber	{10056}
	\s\MYtext	{A seamless toroidal contraption that beeps occasionally. Animals shy away from it. Indestructible.}
}

\NEW{Item}{\iBlankCard}{
	\s\MYname	{}
	\s\MYnumber	{000}
	\s\MYtext	{}
}

\NEW{Item}{\iInvisibilityCloak}{
	\s\MYname	{Invisibility Cloak}
	\s\MYnumber	{10057}
	\s\MYtext	{This cloak enables the wearer to become invisible for five minutes or until they interact with a person or item. Consume when used.}
}

\NEW{Item}{\iCloakingDevice}{
	\s\MYname	{Cloaking Device}
	\s\MYnumber	{10058}
	\s\MYtext	{Using this device renders the user invisible for five minutes or until they interact with a person or item. Consume when used.}
}

\NEW{Item}{\iTruthPotion}{
	\s\MYname	{Vial of Golden Liquid}
	\s\MYnumber	{10059}
	\s\MYtext	{Consuming this liquid obligates the drinker to answer truthfully to 3 yes or no questions. Consume when used.}
}

\NEW{Item}{\iTruthSerum}{
	\s\MYname	{Test Tube of Golden Liquid}
	\s\MYnumber	{10060}
	\s\MYtext	{Consuming this liquid obligates the drinker to answer truthfully to 3 yes or no questions. Consume when used.}
}

\NEW{Item}{\iMagicPoison}{
	\s\MYname	{Vial of Black Liquid}
	\s\MYnumber	{10061}
	\s\MYtext	{Consuming this liquid wounds the drinker. Consume when used.}
}

\NEW{Item}{\iTechPoison}{
	\s\MYname	{Test Tube of Black Liquid}
	\s\MYnumber	{10062}
	\s\MYtext	{Consuming this liquid wounds the drinker. Consume when used.}
}

\NEW{Item}{\iStrengthSpell}{
	\s\MYname	{Strength Spell Stone}
	\s\MYnumber	{10063}
	\s\MYtext	{A glowing black stone. Use by incanting the words "strength flow through me." You will feel warmth run through your veins. After using, you will be able to carry items adding up to 6 hands bulky for a period of five minutes. Consume when used.}
}

\NEW{Item}{\iSteroids}{
	\s\MYname	{Steroids}
	\s\MYnumber	{10064}
	\s\MYtext	{A syringe filled with yellow liquid. Inject to use. After using, you will be able to carry items adding up to 6 hands bulky for a period of five minutes. Consume when used.}
}

\NEW{Item}{\iCRUpPotion}{
	\s\MYname	{Vial of Bright Red Liquid}
	\s\MYnumber	{10065}
	\s\MYtext	{Drinking this liquid will make you feel stronger. The drinker's CR will increase by 1 for a period of five minutes. Consume when used.}
}

\NEW{Item}{\iCRUpSerum}{
	\s\MYname	{Test Tube of Bright Red Liquid}
	\s\MYnumber	{10066}
	\s\MYtext	{Drinking this liquid will make you feel stronger. The drinker's CR will increase by 1 for a period of five minutes. Consume when used.}
}

\NEW{Item}{\iCRDownPotion}{
	\s\MYname	{Vial of Deep Blue Liquid}
	\s\MYnumber	{10067}
	\s\MYtext	{Drinking this liquid will make you feel weaker. The drinker's CR will decrease by 1 for a period of five minutes. Consume when used.}
}

\NEW{Item}{\iCRDownSerum}{
	\s\MYname	{Test Tube of Deep Blue Liquid}
	\s\MYnumber	{10068}
	\s\MYtext	{Drinking this liquid will make you feel weaker. The drinker's CR will decrease by 1 for a period of five minutes. Consume when used.}
}

\NEW{Item}{\iRabbitsFoot}{
	\s\MYname	{Rabbit's Foot}
	\s\MYnumber	{10073}
	\s\MYtext	{The severed foot of a rabbit. Good luck!}
}
\NEW{Item}{\iTranceDrug}{
	\s\MYname	{Trance Prevention Drug}
	\s\MYnumber	{10074}
	\s\MYtext	{A small pill. Taking this will prevent the taker from entering a trance for half an hour. Consume when used.}
}

\NEW{Item}{\iHealthPotion}{
	\s\MYname	{Vial of Bright Green Liquid}
	\s\MYnumber	{10075}
	\s\MYtext	{This potion will heal a wounded person. Consume when used.}
}

\NEW{Item}{\iHealthRemedy}{
	\s\MYname	{Test Tube of Bright Green Liquid}
	\s\MYnumber	{10076}
	\s\MYtext	{This remedy will heal a wounded person. Consume when used.}
}


\NEW{Item}{\iKOSpell}{
	\s\MYname	{Knockout Spell Stone}
	\s\MYnumber	{10069}
	\s\MYtext	{A glowing white stone. Consume when used.}
	\s\MYabils	{\ability{Knockout Spell}{Incant the words "may darkness consume you" and point at the person you wish to knock out.}{You are knocked out.}
	}
}

\NEW{Item}{\iSonicKO}{
	\s\MYname	{Sonic Knockout Device}
	\s\MYnumber	{10070}
	\s\MYtext	{A handheld device with a funnel at one end and a bright red button. Consume when used.}
	\s\MYabils	{\ability{Sonic Knockout}{Point the open end of the device at the person you wish to knock out and press the button.}{You are knocked out.}}
}

\NEW{Item}{\iMCSpell}{
	\s\MYname	{Mind Control Spell Stone}
	\s\MYnumber	{10071}
	\s\MYtext	{A glowing gray stone. Consume when used.}
	\s\MYabils	{\ability{Mind Control Spell}{Incant the words "bend to my will" and point at the person you wish to mind control. They will have to obey your commands for a period of five minutes and cannot harm you during that time.}{You must do everything I say for five minutes. You must not cause any harm to me during this time.}
	}
}

\NEW{Item}{\iMCDevice}{
	\s\MYname	{Mind Control Device}
	\s\MYnumber	{10072}
	\s\MYtext	{A handheld device with an antenna at one end and a bright red button. Consume when used.}
	\s\MYabils	{\ability{Mind Control}{Point the antenna of the device at the person you wish to mind control and press the button. They will have to obey your commands for a period of five minutes and cannot harm you during that time.}{You must do everything I say for five minutes. You must not cause any harm to me during this time.}}
	}

\NEW{ItemLabel}{\iMagicGun}{
	\s\MYname	{Alchemic Accelerator}
	\s\MYnumber	{10076}
	\s\MYtext	{Magical weapon. Can only be used by those with at least 2 mana when $\mu$ is 1 or higher.}
}

\NEW{ItemLabel}{\iTechGun}{
	\s\MYname	{Tesla Phaser}
	\s\MYnumber	{10077}
	\s\MYtext	{High tech weapon. Can only be used by those with at least 2 charge when $\tau$ is 1 or higher.}
}

\NEW{ItemLabel}{\iUpgradedMagicGun}{
	\s\MYname	{Ultra Alchemic Accelerator}
	\s\MYnumber	{10078}
	\s\MYtext	{High powered magical weapon. Gives user a CR +1. Can only be used by those with at least 3 mana when $\mu$ is 2 or higher.}
}

\NEW{ItemLabel}{\iUpgradedTechGun}{
	\s\MYname	{Ultra Tesla Phaser}
	\s\MYnumber	{10079}
	\s\MYtext	{High powered high tech weapon. Gives user a CR +1. Can only be used by those with at least 3 charge when $\tau$ is 2 or higher.}
}

\NEW{ItemLabel}{\iSmallEscapePod}{
	\s\MYname	{One Person Escape Pod}
	\s\MYnumber	{10080}
	\s\MYtext	{This escape pod will allow the rider to escape to a randomly chosen parallel universe. Using this item will remove the rider from gamespace.}
}

\NEW{ItemLabel}{\iLargeEscapePod}{
	\s\MYname	{Two Person Escape Pod}
	\s\MYnumber	{10081}
	\s\MYtext	{This escape pod will allow up to 2 people to escape to a randomly chosen parallel universe. Using this item will remove the riders from gamespace.}
}

\NEW{ItemPacket}{\iTestPacket}{
  \s\MYname	{Test Item}
  \s\MYnumber	{0000}
  \s\MYtext	{A Test Item with a big red button.  Open packet if
		you press the big red button.}
  \s\MYcontents	{The item beeps at you.}
  }

\NEW{ItemFold}{\iTestFold}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{ItemEnvelope}{\iTestEnvelope}{
  \s\MYname	{Test Food}
  \s\MYnumber	{0000}
  \s\MYtext	{open if you eat}
  \s\MYcontents	{It tastes yummy.}
  }

\NEW{ItemLabel}{\iTestLabel}{
  \s\MYname	{Test Gun Label}
  \s\MYnumber	{0000}
  \s\MYtext	{Disc gun, loadable to 20 shots.}
  }

\NEW{Item}{\iWhatzit}{
  \s\MYname	{Whatzit}
  \s\MYnumber	{12345}
  \s\MYtext	{If you press it, open packet a.  If you twirl it, open
		packet b.  If you pull it, open packet c.}
  \bulky	{1}
  \s\MYsigns	{\signstrip{a}{it goes ``beep.''}
		\signstrip{b}{it goes ``whoop.''}
		\signstrip{c}{it goes ``bang.''}
		}
  \s\MYabils	{\ability{Stop Crying}{By futzing with the Whatzit, you
		can make babies stop crying.}{I make the baby stop
		crying.}
		}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
