%%%%%
%%
%% Greensheets live in this directory.  This file doubles as a
%% latex'able example greensheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Greensheet macros (in ../Lists/green-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given greensheet, which will generate
%% the greensheet's name as specified in green-LIST.tex.  However, you
%% can also just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[green]{guildcamp3}
\begin{document}

\name{\gAddPartsMagic{}}


If you have this greensheet, you know how to find the parts needed to run the machine in order to figure out the necessary artifact order. You know that there are three parts needed to produce the correct answer and that they represent three different important essences of the Magical World.

\begin{enumerate}
	\item Something representing magical wonder
	\item Something representing magical faith
	\item Something representing magical strength
\end{enumerate}

In order to get the machine to spit out the correct answers you will have to determine which of those objects are needed. Maybe you'll find some inventorying what's still around. 

Once the machine is built and you have the parts, bring them to the machine. Set them in a triangular shape around the outside of the machine and keep them there for five minutes. This will consume four units of $\alpha$. You may distribute them as you see fit amongst present PCs.

\emph{out of game: You can confirm with a GM that the items you found are things that will work. A GM should be present to check the output of the machine.}


% ans: stardust, dragon skin, and holy water

\end{document}


