%%%%%
%%
%% Greensheets live in this directory.  This file doubles as a
%% latex'able example greensheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Greensheet macros (in ../Lists/green-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given greensheet, which will generate
%% the greensheet's name as specified in green-LIST.tex.  However, you
%% can also just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[green]{guildcamp3}
\begin{document}

\name{\gBatterycharge{}}


\bigquote{``I once bought my kids a set of batteries for Christmas with a note on it saying, toys not included.''}{-- Bernard Manning}

If you have this sheet, then you know how to charge batteries. There are two ways to charge batteries. One way is slower, but doesn't destroy any resources. The other is much faster and more powerful, but destroys weapons in the process. Only the technician can use the fast method. 

In this hyper-advanced world, each person has their own private battery. Recharging it is critical to allowing day-to-day activities. Battery is represented by your $\omega$ level. You may never have more than the starting amount on your character sheet, but you may transfer it to other PCs freely.


\begin{enum}[The slow, nondestructive way]
  \item Go to your work bench (room 200-032) with a screwdriver, and a multitool.
  \item If you are \cTech{}, spend 2 minutes working with the screwdriver and multitool. Otherwise, spend 5 minutes working.
  \item For each two minutes spent, regain 1 unit of battery (one $\omega$)
  \item You can continue to charge the battery at the rate of one charge unit per 5 minutes. 
\end{enum}

\begin{enum}[The fast way which destroys weapons]
	\item Procure a weapon (magic or tech) and a multitool and the device you would like to charge.
	\item Spend 2 minutes working on the weapon. 
	\item If you are the technician, this extracts 3 units of charge (three $\omega$)that you can put into any available battery/batteries. 
	\item This now destroys the weapon (regardless of whether you got any charge from it). Tear up the item card. 
\end{enum}

\end{document}


