
\documentclass[green]{guildcamp3}
\begin{document}
	
	\name{\gManaRecharge{}}
	
	
	
	
	
	If you have this green sheet then you have the ability to recharge your mana and transfer it to other people.
	You may use this mechanic to recharge your personal mana reserves. You must go into a trance in order to recharge mana, as this is how you commune with the gods who bless you with mana. 	During a trance, the person becomes unaware of their surroundings and frozen in place for the duration of the trance. During this time, they may have no intentional interactions with anything and others should regard them as a restrained person. This mana can be transfered to anyone who has a magical core. 
	
	Mana is represented by your $\alpha$ level. You may never have more than the starting amount on your character sheet, but you may transfer it to other PCs freely.
	
	
	
	
	\begin{enum}[Directions]
		\item If you are \cPaladin{} you can recharge at a rate of 1 mana unit per two minute Trance otherwise it takes 5 min to get one unit 
		\item Freeze in place for one minute or five, if anyone tries to interact with you show them the ability card 'Trance'. After one minute resume your previous activities. Unless someone tells you, you don't recall any of what happened during the trance.
		\item To transfer mana you must be within one zoc of the person and the person must be willing, you declare how much mana you transfer
		\item Performing sermons and speeches is rather draining. If/when you do this, you must enter into a trance immediately afterwards for two minutes. This enables you to fully convene with the gods. 
	\end{enum}
	

\end{document}

