\documentclass[green]{guildcamp3}
\begin{document}
	
	\name{\gMPublishing{}}
	
	\cenquote{``Publish or perish.''}{-- Unknown}
	
	
	If you are receiving this greensheet, you are a mage interested in one-upping the other mages. There are several ways you can get points towards this. The ultimate goal is to be the one who gets your name on the Scription of excellent Mastery of the Arcane the most times.
	
	The first way to get your name on the list is by putting the most components into the machine that the scientists and mages are building to generate the answers as to how to save the world.
	
	The second is by being the first to create various different spells and potions. The spells and potions you can create include:
	%\iHealthPotion{}\iHealthRemedy{}\iTranceCure{}\iInvisibilityCloak{}\iCloakingDevice{}\iTruthPotion{}\iTruthSerum{}\iMagicPoison{}\iTechPoison{}\iStrengthSpell{}\iSteroids{}\iCRUpPotion{}\iCRUpSerum{}\iCRDownPotion{}\iCRDownSerum{}\iKOSpell{}\iSonicKO{}\iMCSpell{}\iMCDevice{}\iUpgradedTechGun{}\iUpgradedMagicgun{}\iSmallEscapePod{}\iLargeEscapePod{}
	
	Health Potion (item \iHealthPotion{\MYnumber})
	
	Invisibility Cloak (item \iInvisibilityCloak{\MYnumber})
	
	Truth Potion (item \iTruthPotion{\MYnumber})
	
	Poison (item \iMagicPoison{\MYnumber})
	
	Strength Spell (item \iStrengthSpell{\MYnumber})
	
	Boosting Potion (item \iCRUpPotion{\MYnumber})
	
	Harming Potion (item \iCRDownPotion{\MYnumber})
	
	Knock-out spell (item \iKOSpell{\MYnumber})
	
	Mind-control spell (item \iMCSpell{\MYnumber})
	
	Super-wand (item \iUpgradedMagicGun{})
	
	
	\begin{enum}[Directions]
		\item Complete one of the things that lets you put your name on the list first.
		\item Write your name on the list. Whoever gets there first gets the spot. 
		\item Repeat until you are the best scientist of them all!
	\end{enum}
	
	
\end{document}

