%%%%%
%%
%% Greensheets live in this directory.  This file doubles as a
%% latex'able example greensheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Greensheet macros (in ../Lists/green-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given greensheet, which will generate
%% the greensheet's name as specified in green-LIST.tex.  However, you
%% can also just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[green]{guildcamp3}
\begin{document}

\name{\gSaveWorld{}}


\bigquote{``The end of the world is on people's minds. We have the power to destroy or save ourselves, but the question is what do you do with that responsibility.''}{-- Nicolas Cage}

As everyone here is aware, the end of the world is upon us. Both \bMagicWorld{} and \bTechWorld{} have discovered this and in parallel attempts to save themselves have gathered here together today. Your world has discovered three large artifacts which are critical to ensuring your worlds safety. However, a total of three pairs of items are required. Once all six of these items are procured they must be paired correctly in the correct room at the correct time. At the world ending time, the universe will check on the configuration of the artifacts and determine what will happen. 

Now, everyone is aware of these artifacts but not how to put them together. Between you all, you will be able to figure out what artifacts are needed and in what order they must be placed. Each of \bTechWorld{} and \bMagicWorld{} has planned for this day extensively and has experts available working on this problem. 

Unfortunately, it seems that even if the artifact order is properly achieved, the world's fate is still uncertain. The more people who help with ensuring the safety of the world, the more likely the artifacts are to achieve their success. To help achieve success, form a hand held ring around the artifacts at the world ending moment (T+4:00). Success will be determined based off a sum of the number of people in the ring and a D4. 


\begin{enum}[Directions]
  \item Procure the six artifacts. Your world had three such artifacts.  
  \item Go to the dedicated assembly location (200-002)
  \item Assemble the artifacts in the correct set of pairs.
  \item Ensure the artifacts are assembled correctly at the world ending moment (game time T+4:00). 
\end{enum}


\end{document}


