%%%%%
%%
%% Greensheets live in this directory.  This file doubles as a
%% latex'able example greensheet.
%%
%% _template.tex serves as a bare-bones template suitable for
%% copying when starting a new sheet.
%%
%% Greensheet macros (in ../Lists/green-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \name{...} probably
%% should be the macro for the given greensheet, which will generate
%% the greensheet's name as specified in green-LIST.tex.  However, you
%% can also just use \name{Some Text} if you want.
%%
%%%%%

\documentclass[green]{guildcamp3}
\begin{document}

\name{\gSaveTheWorldMages{}}


\bigquote{``Use this macro for large quotes of prose and such.  It
justifies everything like a paragraph, except with no
indentation.''}{-- The Author}

\cenquote{``This macro is good\\ For shorter quotes\\ Or things like
song lyrics:\\ It centers.''}{-- The Author}


\TODO{This is a test greensheet.}

If you are receiving this greensheet, then you have are involved in the research on how to avoid the end of the Magical World. You have an outline for completing your research, but unfortunately your research will no longer be sufficient given the state of the convergence. You will have to cooperate with the scientists present in order to complete the tasks. 

% 2 pixie wings
Item 1: ... of ... ... ... ... ..., ... ... ... ... ...,

% 1 werewolf fang
Item 2: .. of .. .. .. .. .. .. .. ..  ,  .. .. .. ..

% 1 phoenix feather
Item 3: .. of .. .. .. .. .. .. ..  , .. .. .. .. .. .. ..

% 1 sheet of scrap metal
Item 4: .. of .. .. .. .. ..  ,  .. .. .. .. ..

% 1 soul gem
Item 5: The solution to the word search: .. .. .. ..  ,  .. .. ..



You will also need a \iCauldron{}, \iPlumbicRod{}, and two technical items to complete the assembly. 


\begin{enum}[Directions]
  \item Determine the items needed to build the machine. You will need all of the technical items and all of the magical items. 
  \item Write these into the proposal whitesheet. 
  \item Get this proposal signed by the current highest represented official of both the Magic and the Tech world. Also, get it checked by a GM.
  \item Find all of the required items and bring them to the lab space in 200-002.
  \item Arrange all of the items on the table. With at least one scientist and one mage present, spend five minutes working on the items using the four assembly tools. This process consumes 7 units of $\alpha$ and 7 units of $\omega$. These units can come from anyone present. 
  \item After five minutes, the machine will be complete. Destroy items 1-5 from both the Magic and Technical Worlds. The machine is indestructible. You can now use it to input in items and retrieve orders for the artifacts. 
  
\end{enum}


\end{document}


