
\documentclass[green]{guildcamp3}
\begin{document}
	
	\name{\gSciLicense{}}
	
	Only the Undersecretary of Technology, \cPoliTwo{} is able to issue scientific licenses. In \bTechWorld{}, scientific licenses are critical to ensuring scientific advancement does not go in the wrong direction and enable advancement. The process for obtaining such a license is very long and detailed so as to ensure maximum safety. 
	
	As someone with a license, you are also responsible for ensuring your license(s) are being used responsibly and for reporting any which are being used in non-scientific or harmful to \bTechWorld{} ways. Additionally, you should report any unlicensed research being performed, especially of the sort that may bring harm to \bTechWorld{}.
	
	\begin{enum}[Currently Licensed Scientific Researchers]
		\item \cSciOne{\intro}
		\item \cSciTwo{\intro}
	\end{enum}	
	
	
	\begin{enum}[Issuing new licenses]
		\item Anyone wanting a license must first fill out form GS-1052 and submit it by mail to the Office for Scientific Research. 
		\item The Undersecretary of Technology will review the application, speak to three references and send a representative to visit their proposed laboratory space and go over technical drawings of what they plan to include. 
		\item If after reviewing the application, interviewing the three references and reading the report from the laboratory visit the person is deemed eligible for a license, they are placed on the waiting list.
		\item After waiting for one month on the list, if they are still deemed worthy of a license, the Undersecretary of Technology may issue one. This comes with a battery upgrade that will increase the licensee's $\omega$ by three. 
	\end{enum}
	
	\begin{enum}[Reporting licenses]
		\item To report a scientific license, you must begin by writing a document detailing the reasons why their research is objectionable.  
		\item After writing the document, you must get three additional people to sign the document, each verifying that they personally have observed objectionable research from the licensee.
		\item Formally inform the licensee (in writing) of the fact that their science and/or research is objectionable. 
		\item Submit the report to the Undersecretary of Technology who will decide on further action. 
	\end{enum}

\end{document}

