\documentclass[green]{guildcamp3}
\begin{document}
	
	\name{\gSPublishing{}}
	
	\cenquote{``Publish or perish.''}{-- Unknown}
	
	
	If you are receiving this greensheet, you are able to participate in the publishing race between the scientists somehow. There are several ways to participate in this race. The ultimate goal is to be the one who gets your name on the Official List of Good Experiments the most times. This is not \emph{just} a way to prove you're a good scientist - it's the way to land yourself next in line for the Undersecretary of Science position. As the Undersecretary of Science you'd have incredible control over all the science done on \bTechWorld{}. Wouldn't that be awesome?
	
	The first way to get your name on the list is by putting the most components into the machine that the scientists and mages are building to generate the answers as to how to save the world.
	
	The second is by being the first to create various different objects. The objects you can create include:
	%\iHealthPotion{}\iHealthRemedy{}\iTranceCure{}\iInvisibilityCloak{}\iCloakingDevice{}\iTruthPotion{}\iTruthSerum{}\iMagicPoison{}\iTechPoison{}\iStrengthSpell{}\iSteroids{}\iCRUpPotion{}\iCRUpSerum{}\iCRDownPotion{}\iCRDownSerum{}\iKOSpell{}\iSonicKO{}\iMCSpell{}\iMCDevice{}\iUpgradedTechGun{}\iUpgradedMagicgun{}\iSmallEscapePod{}\iLargeEscapePod{}

	Health Remedy (item \iHealthRemedy{\MYnumber})
	
	Cloaking Device (item \iCloakingDevice{\MYnumber})
	
	Poison (item \iTechPoison{\MYnumber})
	
	Truth Serum (item \iTruthSerum{\MYnumber})
	
	Steroids (item \iSteroids{\MYnumber})
	
	Boosting serum (item \iCRUpSerum{\MYnumber})
	
	Harming serum (item \iCRDownSerum{\MYnumber})
	
	Knock-out serum (item \iSonicKO{\MYnumber})
	
	Mind-control device (item \iMCDevice{\MYnumber})
	
	Super-gun (item \iUpgradedTechGun{})

	
	\begin{enum}[Directions]
		\item Complete one of the things that lets you put your name on the list first.
		\item Write your name on the list. Whoever gets there first gets the spot. 
		\item Repeat until you are the best scientist of them all!
		\item If you're really lucky, become the next Undersecretary of Science...
	\end{enum}
	
	
\end{document}

