\documentclass[green]{guildcamp3}
\documentclass[green]{guildcamp3}
\begin{document}
	
	\name{\gTrance{}}
	
	\cenquote{``This macro is good\\ For shorter quotes\\ Or things like
		song lyrics:\\ It centers.''}{-- The Author}
	
	
	\TODO{Write out how trances effect people. Ability card trance}
	
	If you are receiving this green sheet, then you are a person from the Technical World who is afflicted by trances. The Technical World very much frowns on people with trances, as it views them as unable to control themselves. If you are afflicted by trances and others find out, they will shun you. 
	
	Unfortunately, trances are a fairly severe disorder - without medication they will happen once per half an hour. Luckily, medication can fix this. The medication must be taken every half hour without fail, or the sufferer will fall into a trance. 
	
	During a trance, the sufferer becomes unaware of their surroundings and frozen in place for one minute. During this time, they may have no intentional interactions with anything and others should regard them as a restrained person. 
	
	
	\begin{enum}[If you do not take medication for at least half an hour]
		\item At the half hour mark, stop what you are doing and freeze in place
		\item Remain frozen in place for one minute - if anyone tries to interact with you show them the ability card 'Trance'. 
		\item After one minute resume your previous activities. Unless someone tells you, you don't recall any of what happened during the trance.
		\item Take the medication as soon as possible after this - if you do not, then you will suffer another trance 1/2 hour after the first one began (and so on, until you get the medication).
	\end{enum}
	
	
\end{document}

