\documentclass[green]{guildcamp3}
\begin{document}
	
	\name{\gWedding{}}
		
	If you have this green sheet you then you have the authority and DUTY to perform weddings. When you have two people who wish to be married a short service is required using the following vows. 
	
	Partner 1
	I, PARTNER1NAME take you, PARTNER2NAME, to be my wedded husband/wife. With deepest joy I receive you into my life that together we may be one.I will be to you a loving and faithful husband/wife. I promise you my deepest love, my fullest devotion, my tenderest care. I promise that I will lead our lives into a life of faith and hope. Ever honoring the guidance by the gods through the Word, And so throughout life, no matter what may lie ahead of us, I pledge to you my life as a loving and faithful husband/wife.
	
	Partner 2
	I, PARTNER2NAME, take you, PARTNER1NAME, to be my wedded husband/wife. With deepest joy I receive you into my life that together we may be one.I will be to you a loving and faithful husband/wife. I promise you my deepest love, my fullest devotion, my tenderest care. I promise that I will lead our lives into a life of faith and hope. Ever honoring the guidance by the gods through the Word, And so throughout life, no matter what may lie ahead of us, I pledge to you my life as a loving and faithful husband/wife.
	
	
	"In the presence of our families and friends, I claim you, PARTNE2RNAME, as my lifemate. I belong to you. I offer my life for you. I give to you my protection, my allegiance, my heart, my soul and my body. I take into my keeping the same that is yours. Your life, happiness and welfare will be cherished and placed above my own for all time. You are my lifemate, bound to me for all eternity and always in my care."
	
	"In the presence of our families and friends, I claim you, PARTNER1NAME, as my lifemate. I belong to you. I offer my life to you. I give to you my protection, my allegiance, my heart, my soul and my body. I take into my keeping the same that is yours. Your life, happiness and welfare will be cherished and placed above my own for all time. You are my lifemate, bound to me for alleternity and always in my care."
	
	Both Say the following
	(Name), with this marriage we unite our hearts in tenderness and devotion. We will honor each other's cultures as we join customs to form a trusting relationship. We will protect, support, and encourage each other through life's joys and sorrows as we create a loving future. We promise to establish a home for ourselves and our children shaped by our respective heritages; a loving environment dedicated to peace, hope, and respect for all people. From this day forward our lives will be intertwined forever, blessed in faith, filled with compassion, understanding and love.
	
	
	
	
	\begin{enum}[Directions]
		\item Both people must be willing to perform the ceremony
		\item There must be at least two witnesses to the wedding 
		\item Once both have exchanged vows then you may say "With the power given unto me by the gods I now pronounce you married"

	\end{enum}
	
	
\end{document}

